---
title: "11.1. lmm_baseline_analysis"
author: "Sahar Fatima"
date: "24/08/2020"
output: word_document
mainfont: Times New Roman
fontsize: 12pt 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective
I want to ensure that there are no differences in baseline cheek/brow responding to face/non-face stimuli to allow valid comparison of muscle responding between happy and angry faces or positively- and negatovely-valenced stimuli. 

## Load packages 

```{r message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggeffects)
library(broom.mixed)
library(pixiedust)
library(beepr)
library(ggplot2)
library(lsmeans)
library(emmeans)
library(papaja)
```

## Read in data 
Will read in raw data before z-score transformation and after removing baseline outliers. Will also replace condition codes for readability purposes and add new column with stimulus_type = face/non_face

Note: 429 = angry faces; 673 = happy faces; 913 = negatively-valenced images; 285 = positively-valenced images

```{r message=FALSE, warning=FALSE}

# face data
face_raw <- read_csv(here("R_analysing", "data", "7_face_false.csv")) %>%
  mutate(condition = recode(condition, "429" = "angry","673" = "happy", .default = "NA"))

# non-face data
non_raw <- read_csv(here("R_analysing", "data", "7_non_false.csv")) %>%
  mutate(condition = recode(condition, "913" = "negative","285" = "positive", .default = "NA")) 
  
```

## Filter to keep baseline only
I am only interested in baseline data so will use filter to keep rows where bin_no = 0 (i.e., baseline) for both face and non-face data frames. 

Note: BL = baseline

```{r}
face_BL <- face_raw %>%
  filter(bin_no == 0)

non_BL <- non_raw %>%
  filter(bin_no == 0)
```

## Combine baseline face and baseline non-face data frames
I want to make sure that there are no significant differences between baseline rms cheek and brow scores for face and non-face data. So going to combine face and non-face data frames using bind_rows. Will also arrange by pp_no, stimulus_type, condition, trial and muscle. 

```{r}
face_non_BL <- bind_rows(face_BL, non_BL) %>%
  arrange(pp_no, condition, trial, muscle)

```

## calculate means and standard deviations
Calculate means across stimulus_type, condition and muscle

Adding standard error to summary df. 
```{r}
face_non_BL_summary <- face_non_BL %>%
  group_by(muscle, condition) %>%
  summarise(mean_rms = mean(rms), 
            sd_rms = sd(rms), 
            n = n(), 
            stderr = sd_rms/sqrt(n)) %>%
  arrange(muscle)

face_non_BL_summary$muscle <- fct_relevel(face_non_BL_summary$muscle, c("cheek", "brow")) %>%
  recode("cheek" = "Cheek", "brow" = "Brow")

```

## Graph baseline means 

```{r}
face_non_BL_plot <- face_non_BL_summary %>%
  ggplot(aes(x = condition, y = mean_rms)) +
  geom_bar(aes(fill = condition), 
           stat = "identity", 
           show.legend = FALSE, 
           width = 0.9, 
           position = "dodge") + 
  geom_errorbar(aes(ymin=mean_rms-stderr, ymax=mean_rms+stderr),
                  size=.4,    # Thinner lines
                    width=.2,
                      position=position_dodge(.9)) +
  facet_wrap(vars(muscle), labeller = labeller(muscle = c("brow" = "Brow", "cheek" = "Cheek"))) + 
  theme_apa(base_family = "Arial", box = TRUE) + 
  scale_fill_grey() + 
  facet_wrap(~ muscle) + 
  theme_apa(box = TRUE) + 
  scale_y_continuous(limits = c(0, 12), expand = c(0,0)) + 
  scale_x_discrete(labels = c("angry" = "Angry", "happy" = "Happy", "negative" = "Negative", "positive" = "Positive")) +
  ylab("Mean baseline EMG responding (RMS)") + 
  xlab("Stimulus Type")
  

print(face_non_BL_plot)

ggsave("baseline_lmm.png", path = here("R_analysing", "plots")) 
```

## Moving onto LMM

Although there are differences in brow and cheek responding between happy and angry faces, and positively- and negatively-valenced stimuli - differences don't seem to be significant. However, to be sure going to make LMMs

LMM model structure: This model predicts baseline rms from fixed effects of condition (happy and angry faces, positive and negative images) and muscle (cheek and brow), and their interaction (condition:muscle). 

It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) 

```{r}
glimpse(face_non_BL)

# fix data types

face_non_BL <- face_non_BL %>% mutate_if(is.character, as.factor)

# separate cheek and brow df

cheekBL <- face_non_BL %>%
  filter(muscle == "cheek") 

browBL <- face_non_BL %>%
  filter(muscle == "brow")
```

## CHEEK 

This model predicts baseline cheek RMS from condition (angry, happy, pos, neg) with intercepts for participants
```{r}

options(scipen = 999) # no scientific notation

# cheek_bl_lmm <- lmer(rms ~ condition + stimulus_type + condition*stimulus_type + (1|pp_no), data = cheekBL, REML = FALSE)

cheek_bl_lmm <- lmer(rms ~ condition + (1|pp_no), data = cheekBL, REML = FALSE)


anova(cheek_bl_lmm)
summary(cheek_bl_lmm)


tidy_cheek_bl_lmm <- tidy(cheek_bl_lmm) 

```

### Test contrasts
There does seem to be a sig difference in activity across conditiions. Going to use contrasts to examine these differences. https://rcompanion.org/rcompanion/h_01.html

```{r}
# check levels of condition - to set up contrasts correctly
levels(cheekBL$condition)
```

```{r}

# load library(lsmeans) and library(emmeans)

# obtain group mean estimates 
baseline_cheek <- lsmeans(cheek_bl_lmm, ~ "condition")

# set up contrasts
cheek_contrast <- list(angryvs.happy = c(1, -1, 0, 0), negativevs.positive = c(0, 0, 1, -1), happyvs.neg = c(0, 1, -1, 0), posvs.happy = c(0, 1, 0, -1), posvs.angry = c(1, 0, 0, -1), facevs.nonface = c(1, 1, -1, -1))

cheek_contrasts <- contrast(baseline_cheek, cheek_contrast, adjust = "scheffe")

confint(cheek_contrasts, level = 0.95)


```

## THEN BROW


This model predicts baseline brow RMS from condition (angry, happy, pos, neg) with intercepts for participants
```{r}

options(scipen = 999) # no scientific notation

# brow_bl_lmm <- lmer(rms ~ condition + stimulus_type + condition*stimulus_type + (1|pp_no), data = browBL, REML = FALSE)

brow_bl_lmm <- lmer(rms ~ condition + (1|pp_no), data = browBL, REML = FALSE)

summary(brow_bl_lmm)

tidy_brow_bl_lmm <- tidy(brow_bl_lmm) 
```

### Test contrasts
#### Brow Activity 
There doesn't seem to be a sig difference in activity across conditiions. Going to use contrasts to confirm this. https://rcompanion.org/rcompanion/h_01.html

```{r}
# check levels of condition - to set up contrasts correctly
levels(browBL$condition)
```

```{r}

# load library(lsmeans) and library(emmeans)

# obtain group mean estimates 
baseline_brow <- lsmeans(brow_bl_lmm, ~ "condition")

# set up contrasts
brow_contrast <- list(angryvs.happy = c(1, -1, 0, 0), negativevs.positive = c(0, 0, 1, -1), happyvs.neg = c(0, 1, -1, 0), posvs.happy = c(0, 1, 0, -1), posvs.angry = c(1, 0, 0, -1), facevs.nonface = c(1, 1, -1, -1))

brow_contrasts <- contrast(baseline_brow, brow_contrast, adjust = "scheffe")

confint(brow_contrasts, level = 0.95)

```

# Take home 
For cheek activity, there are no differences in baseline between happy and angry,  but there are between negative and happy AND between postive and negative. 
For brow activity, there are no condition differences in baseline activity.
