---
title: "10_plotting"
author: "Sahar Fatima"
date: "07/07/2020"
output: word_document
mainfont: Times New Roman
fontsize: 12pt 
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

following: https://rpubs.com/jenrichmond/emg6 

## load packages 
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(papaja)
```

## read in screened bin data for faces and non_face

```{r message=FALSE, warning=FALSE}
face_screened <- read_csv(here("R_analysing", "data", "9_face_zdiff_screened.csv"))

non_screened <- read_csv(here("R_analysing", "data", "9_non_zdiff_screened.csv"))
```

## fix bin values 

```{r}
face_screened$bin <- str_sub(face_screened$bin, -4) 

non_screened$bin <- str_sub(non_screened$bin, -4)
```

## recode emotion conditions
```{r}
face_screened <- face_screened %>%
  mutate(condition = recode(condition, "429" = "Angry","673" = "Happy", .default = "NA"))

non_screened <- non_screened %>%
  mutate(condition = recode(condition, "913" = "Negative","285" = "Positive", .default = "NA"))

```

## fix variable types 
```{r}
face_screened$condition <- as.factor(face_screened$condition)
face_screened$trial <- as.factor(face_screened$trial)
face_screened$bin <- as.factor(face_screened$bin)

non_screened$condition <- as.factor(non_screened$condition)
non_screened$trial <- as.factor(non_screened$trial)
non_screened$bin <- as.factor(non_screened$bin)


```

## PLOT FACE

### Average muscle activity during 1000ms (averaging across bin)

```{r}

face_screened$muscle <- factor(face_screened$muscle, levels = c("cheek", "brow"))

bar_face <- face_screened %>%
  group_by(condition, muscle) %>%
   summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = muscle, y = meanZ, group = condition, fill = condition)) + 
  geom_bar(stat = "identity", 
           width = 0.9, 
           position = "dodge") + 
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr),
                  size=.4,    # Thinner lines
                    width=.2,
                      position=position_dodge(.9)) + 
  geom_hline(yintercept = 0) +
  theme_apa(box = TRUE) + 
  theme(legend.title = element_text(hjust = 0.5)) +
  theme(legend.position = c(0.12, 0.82), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'), 
        legend.title = element_blank()) + 
  scale_x_discrete(labels = c("brow" = "Brow", "cheek" = "Cheek")) +
  scale_y_continuous(limits = c(-0.15, 0.10), expand = c(0,0)) + 
  scale_fill_grey(end = 0.7, start = 0.4) +
  xlab("Face Muscle") + 
  ylab("Mean z-score difference (RMS) from baseline \n (averaged across bin)") 
  
bar_face

ggsave("face_stimulus_plot.png", path = here("R_analysing", "plots")) 

```

### CHEEK - Changes in Facial muscle activity over time
```{r}

face_cheek_plot <- face_screened %>%
  filter(muscle == "cheek") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    # Thinner lines
                    width=.2) + 
  theme_apa(box = TRUE) +
  theme(legend.position = c(0.15, 0.8), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'),
        legend.key.height = unit(0.5, "cm"), 
        legend.title = element_blank()) + 
  ylab("Mean differences in cheek activity \n (baseline-corrected z-score)") + 
  xlab("Time after stimulus presentation (ms)") +
  scale_x_discrete(labels = c("bin1" = "100","bin2" = "200", "bin3" = "300","bin4" = "400", "bin5" = "500", "bin6" = "600", "bin7" = "700", "bin8" = "800", "bin9" = "900", "in10" = "1000")) +
  scale_y_continuous(limits = c(-0.2, 0.3)) + 
  scale_color_grey(end = 0.7)

print(face_cheek_plot)

ggsave("face_cheek_plot.png", path = here("R_analysing", "plots")) 
```


### BROW - responding over time
```{r}

face_brow_plot <- face_screened %>%
  filter(muscle == "brow") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    # Thinner lines
                    width=.2) + 
  theme_apa(box = TRUE) +
  theme(legend.position = c(0.15, 0.8), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'),
        legend.key.height = unit(0.5, "cm"), 
        legend.title = element_blank()) + 
  ylab("Mean differences in brow activity \n (baseline-corrected z-score)") + 
  xlab("Time after stimulus presentation (ms)") +
  scale_x_discrete(labels = c("bin1" = "100","bin2" = "200", "bin3" = "300","bin4" = "400", "bin5" = "500", "bin6" = "600", "bin7" = "700", "bin8" = "800", "bin9" = "900", "in10" = "1000")) +
  scale_y_continuous(limits = c(-0.3, 0.25)) + 
  scale_color_grey(end = 0.7)

print(face_brow_plot)

ggsave("face_brow_plot.png", path = here("R_analysing", "plots")) 

```

## NON-FACE

### Activity avg.d across bin - Cheek and Brow 

```{r}
non_screened$muscle <- factor(non_screened$muscle, levels = c("cheek", "brow"))

bar_non <- non_screened %>%
  group_by(condition, muscle) %>%
   summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = muscle, y = meanZ, group = condition, fill = condition)) + 
  geom_bar(stat = "identity", 
           width = 0.9, 
           position = "dodge") + 
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr),
                  size=.4,    # Thinner lines
                    width=.2,
                      position=position_dodge(.9)) + 
  geom_hline(yintercept = 0) +
  theme_apa(box = TRUE) + 
  theme(legend.position = c(0.83, 0.20), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'), 
        legend.title = element_blank()) + 
  scale_x_discrete(labels = c("brow" = "Brow", "cheek" = "Cheek")) +
  scale_y_continuous(limits = c(-0.15, 0.1), expand = c(0,0)) + 
  scale_fill_grey(end = 0.7, start = 0.4) +
  xlab("Face Muscle") + 
  ylab("Mean z-score difference (RMS) from baseline \n (averaged across bin)") 
  

bar_non

ggsave("non_stimulus_plot.png", path = here("R_analysing", "plots")) 

```

### CHEEK - responding over time
```{r}

non_cheek_plot <- non_screened %>%
  filter(muscle == "cheek") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    # Thinner lines
                    width=.2) + 
  theme_apa(box = TRUE) +
  theme(legend.position = c(0.15, 0.8), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'),
        legend.key.height = unit(0.5, "cm"), 
        legend.title = element_blank()) + 
  ylab("Mean differences in cheek activity \n (baseline-corrected z-score)") + 
  xlab("Time after stimulus presentation (ms)") +
  scale_x_discrete(labels = c("bin1" = "100","bin2" = "200", "bin3" = "300","bin4" = "400", "bin5" = "500", "bin6" = "600", "bin7" = "700", "bin8" = "800", "bin9" = "900", "in10" = "1000")) +
  scale_y_continuous(limits = c(-0.2, 0.2)) + 
  scale_color_grey(end = 0.7)

print(non_cheek_plot)

ggsave("non_cheek_plot.png", path = here("R_analysing", "plots")) 

```


## BROW - activity across time
```{r}

non_brow_plot <- non_screened %>%
  filter(muscle == "brow") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    # Thinner lines
                    width=.2) + 
  theme_apa(box = TRUE) +
  theme(legend.position = c(0.15, 0.15), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'),
        legend.key.height = unit(0.5, "cm"), 
        legend.title = element_blank()) + 
  ylab("Mean differences in brow activity \n (baseline-corrected z-score)") + 
  xlab("Time after stimulus presentation (ms)") +
  scale_x_discrete(labels = c("bin1" = "100","bin2" = "200", "bin3" = "300","bin4" = "400", "bin5" = "500", "bin6" = "600", "bin7" = "700", "bin8" = "800", "bin9" = "900", "in10" = "1000")) +
  scale_y_continuous(limits = c(-0.2, 0.2)) + 
  scale_color_grey(end = 0.7)

print(non_brow_plot)

ggsave("non_brow_plot.png", path = here("R_analysing", "plots")) 

```




