---
title: "1_clean all dynamic files"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# load packages
```{r message=FALSE, warning=FALSE}
library(readxl)
library(tidyverse)
library(here)
library(janitor)

```

# call functions
```{r}

source(here("analysis", "clean_write_function.R"))

```

Solution from https://stackoverflow.com/questions/47540471/load-multiple-excel-files-and-name-object-after-a-file-name

# set up path and files list


```{r}
filepath <- here("data", "dirty")

file_list <- list.files(path = filepath, pattern='*.xlsx')


```

# 1. map: read, clean, write to csv

This option reads the dirty xlsx files into a list, runs clean_write on that list, which returns exported clean csv files and a list with clean data in each list item. How...?

the map function takes a list (in this case the list of files) and runs a function (in this case read_excel + mutate(filename)) across all of them. 

map will return a list, in this case a list containing each of the read in excel files + a filename column as a separate item. 

purrr loves lists, once all the files are read in as list items, can use map again (or maybe even map_df- which returns a dataframe- see option 2) to run cleanwrite_emg across all items in the list?

#### A. map read_excel

updated 21/5/2020 advice from Jenny Bryan, option 1 https://jenrichmond.github.io/map_excel_reprex/

```{r message=FALSE, warning=FALSE}
list_raw_emg <- file_list %>% 
  map(~ read_excel(path = here("data", "dirty", .x), range = "A4:AE11")  %>%
        mutate("file_name" = .x))

```

```{r}
# get first item of list for testing- looks good
rawemg1 <- list_raw_emg[[1]]
```


#### B. map cleanwrite_emg
Run cleanwrite_emg on list of files using map, returns a list. Each item in the list is a cleaned file AND each is written to csv in the clean_data folder. 

```{r}
list_cleanwrite_emg <- list_raw_emg %>%
  map(~ cleanwrite_emg(.x))
```


#### C. Check the list items 

did you get what you want? look at one item from the cleanemg emglist. There should also be clean csv files in your folder. 

```{r}
cleanemg159 <- list_cleanwrite_emg[[159]]
```

YES!

