---
title: "3_baseline screening"
author: "Jen Richmond"
date: "03/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)
```

# read combined clean data 

```{r message=FALSE, warning=FALSE}

clean_data <- read_csv(here("data", "combined", "1_clean_combined.csv"))

```

# select just baseline

Arrange by pp, emotion, muscle. Add an empty bl_outlier column. 

```{r}
bl <- clean_data %>%
  filter(bin == "bin_0") %>%
  arrange(pp_no, emotion,  muscle) %>%
  mutate(bl_outlier = "")

stim <- clean_data %>%
  filter(bin != "bin_0") %>%
  arrange(pp_no, emotion,  muscle) %>%
  mutate(bl_outlier = "")
```


# add mean, sd columns

add mean and sd columns AND TRUE FALSE if bl_rms value is > 1.5sd above the mean for the participant, emotion, muscle
```{r}
bl_screen <- bl %>%
  group_by(pp_no, emotion, muscle) %>%
  mutate(meanRMS = mean(rms), sdRMS = sd(rms)) %>%
  mutate(bl_outlier = if_else(rms > meanRMS + 1.5*sdRMS, "TRUE", "FALSE"))
```

# count how many trials have bad baseline

```{r}
glimpse(bl_screen)

bl_screen$bl_outlier <- as.logical(bl_screen$bl_outlier)

bl_screen %>%
  group_by(pp_no, emotion, muscle) %>%
  summarise(trialcount = n(), trialbad = sum(bl_outlier))
```

# drop extra variables to prep for bl_stim bind 

```{r}
bl_bind <- bl_screen %>%
  select(pp_no:rms, bl_outlier)

stim$bl_outlier <- as.logical(stim$bl_outlier) # bind only works if data type is the same in both dfs, change stim outlier col to logicalback to char
```


Bind bl and stim back together using bind_rows and then sort. Use fill to complete empty cells in the bl_outlier column. 
```{r}
bl_stim <- bind_rows(bl_bind, stim) %>%
  arrange(pp_no, emotion, trial, muscle, bin_no) %>%
   fill(bl_outlier)
```


# filter out whole trials with bl outliers, write to csv

```{r}
no_bl_outliers <- bl_stim %>%
  filter(bl_outlier == FALSE) %>%
  select(-bl_outlier)

no_bl_outliers %>%
  write_csv(here("data", "combined", "2_clean_no_bl_outliers.csv"))

```

# filter keep only outlier trials, write to csv

Just in case you need to refer to which trials were thrown out later
```{r}
just_bl_outliers <- bl_stim %>%
  filter(bl_outlier == TRUE) 

just_bl_outliers %>%
  write_csv(here("data", "combined", "3_clean_just_bl_outliers.csv"))

```

