---
title: "4_calculating_zscores"
author: "Jenny Richmond"
date: "23/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

https://rpubs.com/jenrichmond/emgz 


### load packages 
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(skimr)

options(scipen = 999) #set no scientific notation
```

### The process
- first, make data wide using pivot_wider so that brow and cheek are in columns
- use scale() to transform RMS scores into z scores for each participant.
- then make bin wide so that each row represents a single trial and bins 1-6 are in different columns
- make new column for each bin, calculating the difference between that binZ and baselineZ.
- make z diff scores long again

# how to: calculate zscores

Normally, to center a variable, you would subtract the mean of all data points from each individual data point. With scale(), this can be accomplished in one simple call.

Center variable A using the scale() function

`scale(A, center = TRUE, scale = FALSE)`

You can generate z-scores for variable A using the scale() function

`scale(A, center = TRUE, scale = TRUE)`

## read in data 

```{r message=FALSE, warning=FALSE}
data <- read_csv(here("data", "combined", "2_clean_no_bl_outliers.csv"))
                      
```

### Try it out on one pp first

```{r}
pp403 <- data %>%
  filter(pp_no == "pp403")

# make it wide 
widepp403 <- pp403 %>%
  pivot_wider(names_from = muscle, values_from = rms)

# create new variables called zbrow and zcheek using the scale function and specifying center = TRUE and scale = TRUE

widepp403$zbrow = scale(widepp403$brow, center = TRUE, scale = TRUE)
widepp403$zcheek = scale(widepp403$cheek, center = TRUE, scale = TRUE)

# Check that the mean of the new zbrow and zcheek columns is 0 - this is what we want... 
summary(widepp403)

```


## Now do all the data

make data wide, use mutate to make new z variables
```{r}

data_zscore <- data %>%
  pivot_wider(names_from = muscle, 
              values_from = rms) %>%
  group_by(pp_no) %>%
  mutate(Zbrow = scale(brow, center = TRUE, scale = TRUE)) %>%
  mutate(Zcheek = scale(cheek, center = TRUE, scale = TRUE))
  
summary(data_zscore)
```

> note: can also make new z-variables manually: 

> `data_z_manual <- data_wide %>% 
group_by(pp_no) %>%
mutate(Zbrow = (brow - mean(brow))/sd(brow)) %>%
mutate(Zcheek = (cheek - mean(cheek))/sd(cheek))`



# Calculating Difference Scores 

Need to calculate difference scores from baseline. Need to make BIN wide to allow for calculations across columns. Its a bit difficult to do that for both muscles at the same time, so lets separate and work out the difference scores for brow and cheek separately.

### BROW FIRST

#### Add a muscle column 

Just to make things easier to join back together later
```{r}

brow_z <- data_zscore %>%
  mutate(muscle = "brow") %>%
  select(pp_no, condition, emotion, bin, trial, muscle, Zbrow) 
```

#### Make the bin column wide 

... and rename bin_0 as BL (i.e. baseline)
```{r}
brow_z_wide <- brow_z %>%
  pivot_wider(names_from = bin, 
              values_from = Zbrow) %>%
  rename(BL = bin_0)

```

#### mutate() diff scores 

Use wide columns to calcuate the difference between each bin column and BL, creating a new set of columns starting with “diff”, drop BL column and all columns starting with bin (i.e. raw z scores).

note - This df contains for each bin the difference between stimulus and basline, so POSITIVE difference scores = greater activity during STIM than BL and NEGATIVE difference scores = greater activity during BL than STIM

```{r}
brow_z_diff <- brow_z_wide %>% 
  mutate(diff_bin1 = bin_1 - BL, 
         diff_bin2 = bin_2 - BL,
         diff_bin3 = bin_3- BL, 
         diff_bin4 = bin_4 - BL,
         diff_bin5 = bin_5 - BL, 
         diff_bin6 = bin_6 - BL) %>%
  select(-BL, - starts_with("bin"))
```

#### Make data long again 

```{r}
brow_z_diff_long <- brow_z_diff %>%
  pivot_longer(names_to = "bin", 
               values_to = "Zdiff", 
               diff_bin1:diff_bin6)
  
```

#### checking on missingness
```{r}
library(naniar)

vis_miss(brow_z_diff_long)
```



### NOW CHEEK

#### add a muscle column 

...to make things easier to join back together later
```{r}

cheek_z <- data_zscore %>%
  mutate(muscle = "cheek") %>%
  select(pp_no, condition, emotion, bin, trial, muscle, Zcheek) 

```

#### Make the bin column wide 

...and rename bin_0 as BL (i.e. baseline)
```{r}

cheek_z_wide <- cheek_z %>%
  pivot_wider(names_from = bin, 
              values_from = Zcheek) %>%
  rename(BL = bin_0)
```

#### mutate() diff scores 

- Use wide columns to calcuate the difference between each bin column and BL, creating a new set of columns starting with “diff”, drop BL column and all columns starting with bin (i.e. raw z scores).

note - This df contains for each bin the difference between stimulus and basline, so POSITIVE difference scores = greater activity during STIM than BL and NEGATIVE difference scores = greater activity during BL than STIM

```{r}
cheek_z_diff <- cheek_z_wide %>% 
  mutate(diff_bin1 = bin_1 - BL, 
         diff_bin2 = bin_2 - BL,
         diff_bin3 = bin_3- BL, 
         diff_bin4 = bin_4 - BL,
         diff_bin5 = bin_5 - BL, 
         diff_bin6 = bin_6 - BL) %>%
  select(-BL, - starts_with("bin"))
```
#### make data long again 

```{r}

cheek_z_diff_long <- cheek_z_diff %>%
  pivot_longer(names_to = "bin", 
               values_to = "Zdiff", 
               diff_bin1:diff_bin6)
  
```


# BIND CHEEK AND BROW TOGETHER

```{r}
zdiff_cheek_brow <- bind_rows(cheek_z_diff_long, brow_z_diff_long) %>%
  arrange(pp_no, emotion, trial, muscle, bin)
```

# write to csv 
```{r}
zdiff_cheek_brow %>%
  write_csv(here("data", "combined", "4_zdiff_clean.csv"))
```

