---
title: "5_bin outliers"
author: "Jen Richmond"
date: "05/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)
```

# read combined clean no BL outliers data 

```{r message=FALSE, warning=FALSE}
bins <- read_csv(here("data", "combined", "4_zdiff_clean.csv"))

```

Make new screening column which is TRUE if the zdiff value for a particular bin is greater than 2SD the mean zdiff value for that trial for that participant/emotion/muscle. 

```{r}
bins_out <- bins %>%
  group_by(pp_no, emotion, muscle, trial) %>%
  mutate(meanZdiff = mean(Zdiff), sdZdiff = sd(Zdiff)) %>%
  mutate(bin_outlier = if_else(Zdiff > meanZdiff + 2*sdZdiff, "TRUE", "FALSE"))
```

Make sure the new screen column is logical TRUE FALSE
```{r}
bins_out$bin_outlier <- as.logical(bins_out$bin_outlier)
```

How many bins are bad?

```{r}
outlier_true <- bins_out %>%
  filter(bin_outlier == TRUE)
```


# test on 1 participant, 1 trial

Pick a pp that has an example of bad bins and work out how to make the bad bin value be NA

```{r}
example <- bins_out %>%
  filter(pp_no == "pp401") %>%
  filter(emotion == "626")  %>%
  filter(trial == "trial4")

glimpse(example)
 
```

Use mutate and replace to replace the Zdiff value with NA, if bin_outlier == TRUE
```{r}
                         
test <-  example %>% mutate(Zdiff = replace(Zdiff, bin_outlier == "TRUE", NA))
```

# apply bin screen to to whole dataframe

```{r}
bins_screen <- bins_out %>%
  mutate(Zdiff = replace(Zdiff, bin_outlier == "TRUE", NA))

# fix values in bin column 
bins_screen$bin <- str_sub(bins_screen$bin, -4) 
```

# drop extra columns, write csv

```{r}
bins_screen <- bins_screen %>%
  select(1:7) %>%
  write_csv(here("data", "combined", "5_zdiff_binscreened.csv"))
```

