---
title: "8_brow_analysis"
author: "Jen Richmond"
date: "10/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)

# note if you run LMM with just the lme4 package you wont get any pvalues 

# loading lmerTest as well gets you pvalues when you test anova(model)
```

# read in data

```{r}
df <- read_csv(here("data", "combined", "5_zdiff_binscreened.csv")) 

# fix data types, all chars to factors
df$emotion <- as.factor(df$emotion)

df <- df %>% mutate_if(is.character,as.factor)

glimpse(df)
```


# HAPPY-ANGRY

## BROW
Make dataframe with just happy/angry for BROW
```{r}

dfHA_brow <- df %>%
  filter(emotion %in% c("626", "727")) %>%
  filter(muscle == "brow") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(dfHA_brow)

```

Evidence of mimicry to ANGRY would be evidenced by greater brow acvitity over time (bin) for angry than happy. 

LMM- looking to predict Zdiff from emotion (happy angry), and bin (1-6) and their interaction, allowing intercepts to vary for participant and trial. 

### Using lme4 package  w lmerTest package

#### construct model 
```{r}

lm_model_brow <- lmer(Zdiff ~ emotion + bin + emotion*bin + (1|pp_no) + (1|trial), data=dfHA_brow, REML = FALSE) 

```

#### use anova to estimate effects 
```{r}
anova(lm_model_brow)
```

#### use summary to get coefficients 

```{r}
summary(lm_model_brow)
```


### test brow model assumptions

##### plot residuals + qqplot

```{r}
plot(lm_model_brow)


qqnorm(resid(lm_model_brow))
qqline(resid(lm_model_brow))
```

Yikes qqplot not good, what to do about that....?

### transform to correct normality

Make a new column for log modulus
```{r}
dfHA_brow <- dfHA_brow %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))
```

#### run new model 

```{r}
lm_model_brow_logmod <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1|pp_no) + (1|trial), data=dfHA_brow, REML = FALSE) 
```

##### plot residuals + qqplot

```{r}
plot(lm_model_brow_logmod)


qqnorm(resid(lm_model_brow_logmod))
qqline(resid(lm_model_brow_logmod))
```


# NOTES: How to deal with qqplot problem

qqplots for both brow and cheek suggest that normality assumption is violated. log transform wont work in this case because there are negative values, can't log transform negatives. 

A log modulus transform might work. This transform does a log of the absolute value and then puts the sign back. So negative values still end up negative. 

> = sign(x) * log(1+abs(x))

http://www.statsblogs.com/2014/07/14/a-log-transformation-of-positive-and-negative-values/

http://www.jstor.org/stable/pdf/2986305.pdf
