---
title: "11.3 lmm_non_face_analyses"
author: "Sahar Fatima"
date: "26/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Objective:
This script contains LMMs for cheek and brow responding to non-facial stimuli. 

I will begin with the maximal global model (model that  based on theoretical research - i.e.,  contains variables related to the matter at hand) for cheek and brow responding separately, and if it doesn't converge will simplify. 

## load packages 

```{r message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggeffects)
library(broom.mixed)
library(pixiedust)
library(beepr)
library(apaTables)
```

## read in data 

```{r message=FALSE, warning=FALSE}
non <- read_csv(here("R_analysing", "data", "9_non_zdiff_screened.csv")) %>%
  mutate(condition = recode(condition, "913" = "negative","285" = "positive", .default = "NA"))
```

## fix data types 

```{r}
non$condition <- as.factor(non$condition)

non <- non %>% 
  mutate_if(is.character,as.factor)

non$bin <- fct_relevel(non$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

levels(non$bin)
```

## make cheek and brow data frames
```{r}
#non_cheek 
non_cheek <- non %>%
  filter(muscle == "cheek") %>%
  arrange(pp_no, condition, trial, bin)

#non_brow
non_brow <- non %>%
  filter(muscle == "brow") %>%
  arrange(pp_no, condition, trial, bin)
```


# CHEEK 

### Cheek MODEL 1 (including all main effects and interactions as fixed effects and random slopes)
This model predicts Zdiff from fixed effects of condition (happy, angry) and bin (1-10), and their interactions (condition x bin).

It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition, bin and their interaction (condition*bin). 

```{r}
# did not converge 

# lm_non_cheek_1 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin + condition*bin|pp_no), data = non_cheek, REML = FALSE) 
```

#### Model 1 take home 
Cheek Model 1 did not converge - so going to simplify by removing random slope for the interaction. 

### Cheek MODEL 2 (random slopes for condition and bin)
It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition and bin. 


```{r}
# converges! took some time (15 mins)
# lm_non_cheek_2 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin|pp_no), data = non_cheek, REML = FALSE)
```

##### check if normality assumptions are met 
``` {r}
# plot(lm_non_cheek_2)

# qqnorm(resid(lm_non_cheek_2))
# qqline(resid(lm_non_cheek_2)) # spoiler alert they aren't

```

#### transform to correct normality
Usually we would log transform but the Zdiff includes negative values. Alternative is to use a log modulus transform. This transformation log transforms the absolute value (without the -ve) and then puts the sign back on). 
``` {r}
non_cheek <- non_cheek %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))

# run model again

# lm_non_cheek_2 <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition + bin|pp_no), data = non_cheek, REML = FALSE)
```

#### test assumptions again 

```{r}
# plot(lm_non_cheek_2)

# qqnorm(resid(lm_non_cheek_2))
# qqline(resid(lm_non_cheek_2))

```

### get anova() and summary
```{r}
# use anova to estimate effects
# aov_non_cheek_2 <- anova(lm_non_cheek_2) %>%
  # rownames_to_column() %>%
  # rename(term = rowname)

# use summary to get coefficients
# summary(lm_non_cheek_2)
```


#### model 2 take home 
Model 2 converges - from anova output netierh the main bin or condition effects are significant. 

However, from the summary output we can see that there is a significant difference from baseline (p<0.01) in cheek responding to negatively- and positively-valenced stimuli [I think?].

Going to compare with simpler model to compare fit (with slope for condition only)

### Cheek MODEL 3 (random slopes for condition)
It includes random intercepts for participant (accounting for the potential of some kids to just have more active nons than others) and random slopes for condition.

```{r}
# converges! 
lm_non_cheek_3 <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition|pp_no), data = non_cheek, REML = FALSE)
```

#### compare fit
compare fit with model 2 (random slopes for condition and bin)
```{r}
# AIC(lm_non_cheek_2, lm_non_cheek_3)
```

#### likelihood ratio test
```{r}
# anova(lm_non_cheek_2, lm_non_cheek_3)
```

#### get anova()/ summary
```{r}
# use anova to estimate effects
aov_non_cheek_3 <- anova(lm_non_cheek_3) %>%
  rownames_to_column() %>%
  rename(term = rowname)

anova(lm_non_cheek_3)
# use summary to get coefficients
summary(lm_non_cheek_3)
```


#### model 3 take home 
so Model 3 converges - and is of better fit than Model 2. Main effect for bin is signficiant. 

Main effect of bin is signficant - from summary table we can see that difference in cheek responding from baseline and bin 7 (p<0.05) in response to positively-valenced stimuli (from the the graph 8. calculating_zscores) - suggesting that cheek responding is increasing over time [??]

From summary table, we can see that the difference between baseline cheek resopnding is significantly greater in response to positively- relative to negatively-valenced stimuli (from the the graph 8. calculating_zscores)


Going to compare with simpler model just to compare fit. 

### Cheek MODEL 4 (intercepts only)

```{r}
lm_non_cheek_4 <- lmer(log_modulus ~ condition + bin + condition*bin + (1|pp_no), data = non_cheek, REML = FALSE)
```

#### compare fit
```{r}
AIC(lm_non_cheek_3, lm_non_cheek_4)
```
#### model 4 take home 

Model 3 is better fit than Model 4. 

## Cheek TAKE HOME
Model 3 with fixed effects of condition, bin and their interaction and slopes for condition has best fit. 

Model 3 - main effect for bin is significant. and from summary table diffbin7 and conditionnegative are sig. refer to Modle 3 take home for comments. 

# BROW

### Brow MODEL 1 (including all main effects and interactions as fixed effects and random slopes)
This model predicts Zdiff from fixed effects of condition (happy, angry) and bin (1-10), and their interactions (condition x bin).

It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition, bin and their interaction (condition*bin). 

```{r}
# did not converge 

# lm_non_brow_1 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin + condition*bin|pp_no), data = non_brow, REML = FALSE) 
```

#### Model 1 take home 
Brow Model 1 did not converge - so going to simplify by removing random slope for the interaction. 

### Brow MODEL 2 (random slopes for condition and bin)
It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition and bin. 


```{r}
# failed to converge

lm_non_brow_2 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin|pp_no), data = non_brow, REML = FALSE)
```

##### check if normality assumptions are met 
``` {r}
plot(lm_non_brow_2)

qqnorm(resid(lm_non_brow_2))
qqline(resid(lm_non_brow_2)) # spoiler alert they aren't

```

#### transform to correct normality
Usually we would log transform but the Zdiff includes negative values. Alternative is to use a log modulus transform. This transformation log transforms the absolute value (without the -ve) and then puts the sign back on). 
``` {r}
non_brow <- non_brow %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))

# run model again

# lm_non_brow_2 <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition + bin|pp_no), data = non_brow, REML = FALSE)
```


#### test assumptions again 
Residuals are more evenly distributed than before; qq plot is better as well.

```{r}
# plot(lm_non_brow_2)

# qqnorm(resid(lm_non_brow_2))
# qqline(resid(lm_non_brow_2))

```


#### model 2 take home 
Failed to converge 
Going to compare with simpler model (with slopes for condition only)

### Brow MODEL 3 (slopes for condition)

```{r}
lm_non_brow_3 <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition|pp_no), data = non_brow, REML = FALSE)
```


### get anova()/ summary
```{r}
aov_non_brow_3 <- anova(lm_non_brow_3) %>%
  rownames_to_column() %>%
  rename(term = rowname)


anova(lm_non_brow_3)
summary(lm_non_brow_3)
```

#### model 3 take home
Brow model 3 converges - neither main effects nor interaction are significant. 

### Brow MODEL 4 (intercepts only)

```{r}
lm_non_brow_4 <- lmer(log_modulus ~ condition + bin + condition*bin + (1|pp_no), data = non_brow, REML = FALSE)
```

#### compare fit
```{r}
AIC(lm_non_brow_3, lm_non_brow_4)
```
#### model 4 take home 
Model 3 is better fit than Model 4. 

## Brow TAKE HOME
Model 3 with fixed effects of condition, bin and their interaction, and slopes for condition has best fit. Neither main effects nor interaction are significant
