---
title: "next steps clean data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(naniar)
library(ggbeeswarm)
library(ggeasy)

```

# Read in clean data

```{r}

faces <- read_csv(here("R_cleaning", "data", "clean_data", "faces_clean.csv"))

non <- read_csv(here("R_cleaning", "data","clean_data", "non-faces_clean.csv"))

```

# use naniar to look at missing data


```{r}
naniar::vis_miss(faces)

naniar::vis_miss(non)

```

# create participant and condition columns out of filename

NOTE working with nonface here because it isn't missing data--- you will need to replicate with both face and non face

Use separate() to split the filename into pp_no and condition and mutate with str_sub to drop the last 6 characters off the end of the values in the condition column to get rid of the .xlsx

```{r}

non_cond <- non %>%
  separate(file_name, into = c("pp_no", "condition"), sep = "_") %>% 
  mutate(condition = str_sub(condition, end = -6)) 
```


# Q1 are there baseline differences between brow and cheek?

1. Filter the data to only include bin 0 (baseline- BL) and plot BL scores for each trial, separately for brow and cheek, coloured by positive/negative. 

```{r}
non_BL <- non_cond %>%
  filter(bin == "bin_0")
```

Plot baseline 

```{r}
non_BL %>%
  ggplot(aes(x = trial , y = rms, colour = condition)) +
  geom_quasirandom() + 
  facet_wrap(~ muscle)
```

```{r}
non_BL %>%
  group_by(muscle, trial)  %>%
  summarise(meanRMS = mean(rms), sdRMS = sd(rms))
```
