---
title: "binding_baseline_main"
author: "Sahar Fatima"
date: "20/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r}
library(tidyverse)
library(here)
library(dplyr)
library(ggeasy)
library(skimr)

```


# read in baseline outlier face and non-face, and original face and non-face dataframes 

```{r message=FALSE, warning=FALSE}

face <- read_csv(here("R_cleaning", "data", "clean_data", "faces_clean.csv")) #face data
non <- read_csv(here("R_cleaning", "data", "clean_data", "non-faces_clean.csv")) #non-face data

BL_face <- read_csv(here("R_analysing", "data", "6_face_BL_outlier.csv")) #baseline face
BL_non <- read_csv(here("R_analysing", "data", "6_non-face_BL_outlier.csv")) #baseline non-face 

```

# FACE data 

## make new pp_no and condition variables to match BL data frames
```{r}
face <- face %>%
  separate(file_name, into = c("pp_no", "condition"), sep = "_") %>% 
  mutate(condition = str_sub(condition, end = -6)) 
```

## select variables + filter out BL data from main data frames
```{r}
BL_face_small <- BL_face %>%
  select(1:7, outlier1.5SD)

face_small <- face %>%
  filter(!(bin == "bin_0"))
```

## bind with original data frames and arranging according to pp_no, trial and bin. 
## Filling in outlier variable with true or false depending on whether baseline was an outlier or not. 
#### but before this, I am going to test it on 1 - 2 participants. Choosing pp481, because the pp has a mix of outliers and non-outliers

```{r}
# before binding - make condition character 
BL_face_small$condition <- as.character(BL_face_small$condition)


newBLface <- bind_rows(face_small, BL_face_small) %>%
  arrange(pp_no, condition, muscle, trial, bin_no) %>%
  fill(outlier1.5SD)

pp481_face <- newBLface %>%
  filter(pp_no == "pp481") %>%
  arrange(pp_no, condition, muscle, trial, bin_no) %>%
  fill(outlier1.5SD)


```


# NON-FACE data 

## make new pp_no and condition variables to match BL data frames
```{r}
non <- non %>%
  separate(file_name, into = c("pp_no", "condition"), sep = "_") %>% 
  mutate(condition = str_sub(condition, end = -6)) 
```


## select variables + filter out BL data from main data frames
```{r}
BL_non_small <- BL_non %>%
  select(1:7, outlier1.5SD)

non_small <- non %>%
  filter(!(bin == "bin_0"))
```

## bind with original data frames and arranging according to pp_no, trial and bin. 
## Filling in outlier variable with true or false depending on whether baseline was an outlier or not.
```{r}
# before binding - make condition character 
BL_non_small$condition <- as.character(BL_non_small$condition)

newBLnon <- bind_rows(non_small, BL_non_small) %>%
  arrange(pp_no, condition, muscle, trial, bin_no) %>%
  fill(outlier1.5SD)
```

 
# interim summary 
So far, we have read in the main and BL dataframes, combined them using filter, bind and arrange. Following this, we filled in the oultlier1.5SD variable!

## Going to filter out all instances where outlier1.5SD is TRUE and then using write_csv will write the new face and non-face data frames. going to make a data frame for outliers as well. 

```{r}
# face data frame with BL outliers taken out
face_false <- newBLface %>%
  filter(!(outlier1.5SD == "TRUE")) 

# face data frame containing only BL outliers
face_outlier <- newBLface %>%
  filter(outlier1.5SD == "TRUE")

# non-face data frame with BL outliers taken out
non_false <- newBLnon %>%
  filter(!(outlier1.5SD == "TRUE")) 

# non-face data frame containing only BL outliers
non_outlier <- newBLnon %>%
  filter(outlier1.5SD == "TRUE")
```

### writing csv's
```{r}
write_csv(face_false, path = here("R_analysing", "data", "7_face_false.csv"))

write_csv(face_outlier, path = here("R_analysing", "data", "7_face_outlier.csv"))

write_csv(non_false, path = here("R_analysing", "data", "7_non_false.csv"))

write_csv(non_outlier, path = here("R_analysing", "data", "7_non_outlier.csv"))
```








