---
title: "5_bin_outliers"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages
```{r}
library(tidyverse)
library(here)
library(janitor)
library(tidyr)
library(dplyr)
```


#read in combined clean no BL outliers data 
```{r}
bins <- read_csv(here("rileyraw_data", "adult_child_combined", "zdiff_cheek_brow.csv"))
```

#make new screening column which is TRUE if the zdiff value for a particular bin is greater than 2sd above the mean zdiff value for tha trial for that participant/emotion/muscle
```{r}
bins_out <- bins %>%
  group_by(pp_no, model, emotion, muscle, trial) %>%
  mutate(meanZdiff = mean(zdiff), sdZdiff = sd(zdiff)) %>%
  mutate(bin_outlier = if_else(zdiff > meanZdiff + 2*sdZdiff, "TRUE", "FALSE"))
```

#Make sure the new screen column is logical TRUE FALSE
```{r}
bins_out$bin_outlier <- as.logical(bins_out$bin_outlier)
```

#How many bins are bad?
```{r}
outlier_true <- bins_out %>%
  filter(bin_outlier == TRUE)
```

test on 1 participant, 1 trial 
#pick a pp that has an example of bad bins and work out how to make the bad bin value NA
```{r}
example <- bins_out %>%
  filter(pp_no == "pp406") %>%
  filter(emotion == "121") %>%
  filter(trial == "trial1")

glimpse(example)
```

#use mutate and replace to replace the Zdiff value with NA, if bin_outlier -- TRUE

```{r}
test <- example %>%
  mutate(zdiff = replace(zdiff, bin_outlier == "TRUE", NA))
```

#apply bin screen to whole dataframe
```{r}
bins_screen <- bins_out %>%
  mutate(zdiff = replace(zdiff, bin_outlier == "TRUE", NA))

bins_screen$emotion <- as.character(bins_screen$emotion)


glimpse(bins_screen)
```

#recode emotions 
```{r}

bins_screen$emotion_code <- bins_screen$emotion


child_bins_screen <- bins_screen %>%
  filter(model == "child") %>%
  filter(emotion_code == "child-happy", "child-angry", "child-fear", "child-sad") %>%
  arrange(pp_no, model, emotion, trial, muscle, bin, zdiff)

child_bins_screen$emotion_code <- child_bins_screen$emotion

child_bins_screen <- child_bins_screen %>%
  mutate(emotion_code = recode(emotion, 
                               "121" = "child-happy",
                          "323" = "child-angry",
                          "424" = "child-fear",
                          "525" = "child-sad", .default = "NA")) %>%
  select(pp_no, model, emotion, emotion_code, trial, muscle, bin, zdiff)







bins_screen <- bins_screen %>% 
  mutate(emotion_code = case_when( %in% "131" ~ "adult-happy"
                                                emotion %in% "232" ~ "adult-angry",
                                                emotion %in% "434" ~ "adult-fear",
                                                emotion %in% "535" ~ "adult-sad",
                                                emotion %in% "121" ~ "child-happy"
                                                emotion %in% "323" ~ "child-angry",
                                                emotion %in% "424" ~ "child-fear",
                                                emotion %in% "525" ~ "child-sad",
                                                TRUE ~ "other"))

bins_screen <- bins_screen %>%
  mutate(emotion_code = recode(emotion_code,"131" = "adult-happy",
                          "232" = "adult-angry",
                          "434" = "adult-fear",
                          "535" = "adult-sad",
                          "121" = "child-happy",
                          "323" = "child-angry",
                          "424" = "child-fear",
                          "525" = "child-sad", .default = "NA")) %>%
  select(pp_no, model, emotion, emotion_code, trial, muscle, bin, zdiff)



```


#drop extra columns, write csv
```{r}
bins_screen <- bins_screen %>%
  select(1:8) %>%
  write_csv(here("rileyraw_data", "adult_child_combined", "zdiff_binscreened.csv"))
```

