---
title: "6_plotting"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages
```{r}

library(devtools)

devtools::install_github("crsh/papaja")
```

```{r}
library(tidyverse)
library(here)
library(janitor)
library(papaja)
```


#read bin screened data

```{r}
plot_data <- read_csv(here("rileyraw_data", "adult_child_combined", "zdiff_binscreened.csv"))
```

#fix bin values - drop diff bit from values in bin column, keep the last 4 char from diff_bin1
```{r}
plot_data$bin <- str_sub(plot_data$bin, -4)
```


#fix data type
```{r}
plot_data$emotion <- as.factor(plot_data$emotion)

plot_data$trial <- as.factor(plot_data$trial)

plot_data$bin <- as.factor(plot_data$bin)

plot_data$muscle <- as.factor(plot_data$muscle)

plot_data$emotion_code <- as.factor(plot_data$emotion_code)

glimpse(plot_data)
```
```{r}
levels(plot_data$bin)
```

#BROW-ADULT
##plot brow for adult face data
```{r}
plot_data %>%
  filter(model == "adult", muscle == "brow") %>%
  group_by(emotion_code, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion_code, colour = emotion_code)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))


plot_data %>%
  filter(model == "adult", muscle == "brow") %>%
  filter(emotion_code %in% c("adult-happy", "adult-angry")) %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))


plot_data %>%
  filter(model == "adult", muscle == "brow") %>%
  filter(emotion %in% c("adult-sad", "adult-fear")) %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))


```


#BROW-CHILD
##plot brow for child face data
```{r}
plot_data %>%
  filter(model == "child", muscle == "brow") %>%
  filter(emotion %in% c("child-happy", "child-angry")) %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))


plot_data %>%
  filter(model == "child", muscle == "brow") %>%
  filter(emotion %in% c("child-sad", "child-fear")) %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))


plot_data %>%
  filter(model == "child", muscle == "brow") %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))

```
#CHEEK-ADULT
##plot cheek for adult face data 
```{r}
plot_data %>%
  filter(model == "adult", muscle == "cheek") %>%
  filter(emotion %in% c("adult-happy", "adult-angry")) %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))

plot_data %>%
  filter(model == "adult", muscle == "cheek") %>%
  filter(emotion %in% c("adult-sad", "adult-fear")) %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))


plot_data %>%
  filter(model == "adult", muscle == "cheek") %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```
#CHEEK-CHILD
##plot cheek for child face data 
```{r}
plot_data %>%
  filter(model == "child", muscle == "cheek") %>%
  filter(emotion %in% c("child-happy", "child-angry")) %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))

plot_data %>%
  filter(model == "child", muscle == "cheek") %>%
  filter(emotion %in% c("child-sad", "child-fear")) %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))

plot_data %>%
  filter(model == "child", muscle == "cheek") %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```
#ADULT-CHEEK-BROW

#plot brow and cheek together for adult
```{r}
plot_data %>%
  filter(model == "adult") %>%
  filter(emotion %in% c("adult-happy", "adult-angry")) %>%
  group_by(emotion, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to happy and angry diplayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))

plot_data %>%
  filter(model == "adult") %>%
  filter(emotion %in% c("adult-fear", "adult-sad")) %>%
  group_by(emotion, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to fear and sad diplayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))

plot_data %>%
  filter(model == "adult") %>%
  group_by(emotion, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to fear and sad diplayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```

#CHILD-CHEEK-BROW
##plot brow and cheek together for child
```{r}
plot_data %>%
  filter(model == "child") %>%
  filter(emotion %in% c("child-happy", "child-angry")) %>%
  group_by(emotion, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to happy and angry diplayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))

plot_data %>%
  filter(model == "child") %>%
  filter(emotion %in% c("child-sad", "child-fear")) %>%
  group_by(emotion, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to sad and fear diplayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))

plot_data %>%
  filter(model == "child") %>%
  group_by(emotion, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to sad and fear diplayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```

```{r}
plot_data <- plot_data %>%
  write_csv(here("rileyraw_data", "adult_child_combined", "zdiff_binscreened.csv"))
```

