---
title: "7_analysing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages

```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(ggplot2)
```
#read in data

```{r}
df <- read_csv(here("rileyraw_data", "adult_child_combined", "zdiff_binscreened.csv"))
```

#fix data types, all chars to factors
```{r}
glimpse(df)

df <- df %>% mutate_if(is.character,as.factor)

```

#make dataframe with just happy/angry for cheek for adult faces 
```{r}

adult_cheek <- df %>%
  filter(muscle == "cheek") %>%
  filter(model == "adult") %>%
  arrange(pp_no, model, emotion_code, trial, bin)

glimpse(adult_cheek)


```

#evidence of mimicry to happy would be evidenced by greater cheek activity over time (bin) for happy than angry
##LMM - looking to predict zdiff from emotion (happy, angry), and bin (1-10) and their interaction, allowing intercepts to vary for participant and trial 
```{r}
adultlm_model_cheek <- lmer(zdiff ~ emotion + bin + emotion*bin + (1|pp_no) + (1|trial), data = adult_cheek, REML = FALSE)
```

#use ANOVA to estimate effects 
```{r}
anova(adultlm_model_cheek)

```
#use summary to get coefficients 
```{r}
summary(adultlm_model_cheek)

```
#test cheek model assumptions
##plot residuals 
```{r}
plot(adultlm_model_cheek)

```
#ggplot 
```{r}
qqnorm(resid(adultlm_model_cheek))
qqline(resid(adultlm_model_cheek))
```

#do the same with child face data
```{r}
child_cheek <- df %>%
  filter(muscle == "cheek") %>%
  filter(model == "child") %>%
  arrange(pp_no, model, emotion, trial, bin)

glimpse(child_cheek)
```

```{r}
childlm_model_cheek <- lmer(zdiff ~ emotion + bin + emotion*bin + (1|pp_no) + (1|trial), data = child_cheek, REML = FALSE)
```

```{r}
anova(childlm_model_cheek)
```

```{r}
summary(childlm_model_cheek)
```

```{r}
plot(childlm_model_cheek)
```

```{r}
qqnorm(resid(childlm_model_cheek))
qqline(resid(childlm_model_cheek))
```

#Brow
##make dataframe with just happy/angry BROW
```{r}
adult_brow <- df %>%
  filter(muscle == "brow") %>%
  filter(model == "adult") %>%
  arrange(pp_no, model, emotion, trial, bin)

glimpse(adultHA_brow)
```
```{r}
adultlm_model_brow <- lmer(zdiff ~ emotion + bin + emotion*bin + (1|pp_no) + (1|trial), data = adult_brow, REML = FALSE)
```

```{r}
anova(adultlm_model_brow)
```

```{r}
summary(adultlm_model_brow)
```
```{r}
plot(adultlm_model_brow)
```
```{r}
qqnorm(resid(adultlm_model_brow))
qqline(resid(adultlm_model_brow))
```

#do the same with child faces 
```{r}
child_brow <- df %>%
  filter(muscle == "brow") %>%
  filter(model == "child") %>%
  arrange(pp_no, model, emotion, trial, bin)
```

```{r}
childlm_model_brow <- lmer(zdiff ~ emotion + bin + emotion*bin + (1|pp_no) + (1|trial), data = child_brow, REML = FALSE)
```

```{r}
anova(childlm_model_brow)
```
```{r}
summary(childlm_model_brow)
```

```{r}
plot(childlm_model_brow)
```

```{r}
qqnorm(resid(childlm_model_brow))
qqline(resid(childlm_model_brow))
```

