---
title: "8a_cheek_analysis"
output:
  pdf_document: default
  html_document: default
---
#load packages
```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(pixiedust)
library(beepr)
```

#read in data 
```{r}
df <- read_csv(here("rileyraw_data", "adult_child_combined", "zdiff_binscreened.csv"))

df$emotion <- as.factor(df$emotion)

df <- df %>% mutate_if(is.character, as.factor)

glimpse(df)
```
happy-angry 

#CHILD-CHEEK

#Make df with just happy/angry child face for cheek

```{r}
HA_child_cheek <- df %>%
  filter(emotion %in% c("child-happy", "child-angry")) %>%
  filter(muscle == "cheek") %>%
  filter(model == "child") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(HA_child_cheek)
```

#transform to correct normality

```{r}
HA_child_cheek <- HA_child_cheek %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))
```

##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion and slope for emotion 
```{r}
child_cheek_emo2 <- lmer(log_modulus ~ emotion + (1 + emotion|pp_no), data = HA_child_cheek, REML = FALSE)

beep(1)
```

#just main effect of emotion and bin, and slope for emotion 
```{r}
child_cheek_emo_bin2 <- lmer(log_modulus ~ emotion + bin + (1 + emotion|pp_no), data = HA_child_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion and bin and emotion*bin, and slope for emotion (slope for bin doesnt converge)

```{r}
child_cheek_emo_bin_interaction2 <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 + emotion|pp_no), data = HA_child_cheek, REML = FALSE)

beep(1)
```


#test for best fit 

```{r}
AIC(child_cheek_emo2)

AIC(child_cheek_emo_bin2)

AIC(child_cheek_emo_bin_interaction2)
```

```{r}
anova(child_cheek_emo2, child_cheek_emo_bin2)
```

```{r}
anova(child_cheek_emo_bin2, child_cheek_emo_bin_interaction2)
```


#BEST FIT
##the model with emotion and bin main effects and slope for emotion provides the best fit for the data 

```{r}
child_tidy_cheek2 <- tidy(child_cheek_emo_bin2)

anova(child_cheek_emo_bin2)
```
```{r}
summary(child_cheek_emo_bin2)
```

#really nice table 

```{r}
really_nice_table <- dust(child_cheek_emo_bin2) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```


#ADULT-CHEEK
#now do the same for adult data 

```{r}
HA_adult_cheek <- df %>%
  filter(emotion %in% c("adult-happy", "adult-angry")) %>%
  filter(muscle == "cheek") %>%
  filter(model == "adult") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(HA_adult_cheek)
```

#transform to correct to normality
```{r}
HA_adult_cheek <- HA_adult_cheek %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))
```

##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion and slope for emotion 
```{r}
adult_cheek_emo2 <- lmer(log_modulus ~ emotion + (1 + emotion|pp_no), data = HA_adult_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion and bin, and slope for emotion 
```{r}
adult_cheek_emo_bin2 <- lmer(log_modulus ~ emotion + bin + (1 + emotion|pp_no), data = HA_adult_cheek, REML = FALSE)

beep(1)
```


#main effect of emotion and bin and emotion*bin interaction, and slope for emotion 
```{r}
adult_cheek_emo_bin_interaction2 <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 + emotion|pp_no), data = HA_adult_cheek, REML = FALSE)

beep(1)
```


```{r}
AIC(adult_cheek_emo2)

AIC(adult_cheek_emo_bin2)

AIC(adult_cheek_emo_bin_interaction2)
```

```{r}
anova(adult_cheek_emo2, adult_cheek_emo_bin2)
```


```{r}
anova(adult_cheek_emo_bin2, adult_cheek_emo_bin_interaction2)
```


#BEST FIT
##model with main effects of emotion and bin and slope for emotion provides the best fit 

```{r}
adult_tidy_cheek2 <- tidy(adult_cheek_emo_bin2)
```

```{r}
anova(adult_cheek_emo_bin2)
```
```{r}
summary(adult_cheek_emo_bin2)
```


#tidying model output 

```{r}
terms <- c("intercept", "happy vs. angry", "bin1 vs. bin2", "bin2 vs. bin3", "bin3 vs. bin4", "bin4 vs. bin5", "bin5 vs. bin6")

adult_tidier_cheek2 <- adult_tidy_cheek2 %>%
  filter(effect == "fixed") %>%
  select(-group)


adult_tidier_cheek2 <-  adult_tidier_cheek2 %>%
  mutate(niceterms = c("intercepts", "happy vs. angry", "bin1 vs. bin2", "bin2 vs. bin3", "bin3 vs. bin4", "bin4 vs. bin5", "bin5 vs. bin6", "emotion x bin1-2", "emotion x bin2-3", "emotion x bin3-4", "emotion x bin4-5", "emotion x bin5-6"))
```

#Really nice table 
```{r}
really_nice_table <- dust(adult_cheek_emo_bin2) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```

#ALL_EMO_CHILD

```{r}
child_cheek <- df %>%
  filter(muscle == "cheek") %>%
  filter(model == "child") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(child_cheek)
```


#transform to correct normality

```{r}
child_cheek <- child_cheek %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))
```

##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion and slope for emotion 
```{r}
child_cheek_emo4 <- lmer(log_modulus ~ emotion + (1 + emotion|pp_no), data = child_cheek, REML = FALSE)

beep(1)
```

#just main effect of emotion and bin, and slope for emotion 
```{r}
child_cheek_emo_bin4 <- lmer(log_modulus ~ emotion + bin + (1 + emotion|pp_no), data = child_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion and bin and emotion*bin, and slope for emotion (model failed to converge)

```{r}
child_cheek_emo_bin_interaction4 <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 + emotion|pp_no), data = child_cheek, REML = FALSE)

beep(1)
```


#test for best fit 

```{r}
AIC(child_cheek_emo4)

AIC(child_cheek_emo_bin4)

AIC(child_cheek_emo_bin_interaction4)
```

#anova
```{r}
anova(child_cheek_emo4, child_cheek_emo_bin4)
```

```{r}
anova(child_cheek_emo_bin4, child_cheek_emo_bin_interaction4)
```

#BEST FIT
##the model that provides the best fit for the data is one with a main effect of emotion and bin and a slope for emotion 

```{r}
child_tidy_cheek4 <- tidy(child_cheek_emo_bin4)
```

```{r}
summary(child_cheek_emo_bin4)
```
```{r}
anova(child_cheek_emo_bin4)
```


#really nice table 

```{r}
really_nice_table <- dust(child_cheek_emo_bin4) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```


#ALL_EMO_ADULT

```{r}
adult_cheek <- df %>%
  filter(muscle == "cheek") %>%
  filter(model == "adult") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(adult_cheek)
```

#transform to correct normality

```{r}
adult_cheek <- adult_cheek %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))
```

##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion and slope for emotion (failed to converge)
```{r}
adult_cheek_emo4 <- lmer(log_modulus ~ emotion + (1 + emotion|pp_no), data = adult_cheek, REML = FALSE)

beep(1)
```

#just main effect of emotion and bin, and slope for emotion (failed to converge)
```{r}
adult_cheek_emo_bin4 <- lmer(log_modulus ~ emotion + bin + (1 + emotion|pp_no), data = adult_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion and bin and emotion*bin, and slope for emotion 

```{r}
adult_cheek_emo_bin_interaction4 <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 + emotion|pp_no), data = adult_cheek, REML = FALSE)

beep(1)
```

```{r}
AIC(adult_cheek_emo4)
AIC(adult_cheek_emo_bin4)
AIC(adult_cheek_emo_bin_interaction4)
```


#BEST FIT

##the only model that converged was the one with a main effect of emotion and bin and emotion*bin interaction, and slope for emotion 

```{r}
adult_tidy_cheek4 <- tidy(adult_cheek_emo_bin_interaction4)
```

```{r}
summary(adult_cheek_emo_bin_interaction4)
```

```{r}
anova(adult_cheek_emo_bin_interaction4)
```


#really nice table 

```{r}
really_nice_table <- dust(adult_cheek_emo_bin_interaction4) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```







