---
title: "8b_brow_analysis"
output: html_document
---

#load packages 
```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(pixiedust)
```

#read in data 
```{r}
df <- read_csv(here("rileyraw_data", "adult_child_combined", "zdiff_binscreened.csv"))

df$emotion <- as.factor(df$emotion)

df <- df %>% mutate_if(is.character, as.factor)

glimpse(df)

```

happy-angry 

BROW

#Make df with just happy/angry child face for brow

```{r}
HA_child_brow <- df %>%
  filter(emotion %in% c("child-happy", "child-angry")) %>%
  filter(muscle == "brow") %>%
  filter(model == "child") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(HA_child_brow)
```

#transform to correct normality

```{r}
HA_child_brow <- HA_child_brow %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))
```


##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion 
```{r}
child_brow_emo <- lmer(log_modulus ~ emotion + (1|pp_no), data = HA_child_brow, REML = FALSE)

beep(1)
```

#main effect of emotion and bin

```{r}
child_brow_emo_bin <- lmer(log_modulus ~ emotion + bin + (1|pp_no), data = HA_child_brow, REML = FALSE)

beep(1)
```

#main effect of emotion and bin and bin*emotion interaction

```{r}
child_brow_emo_bin_interaction <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1|pp_no), data = HA_child_brow, REML = FALSE)

beep(1)
```



```{r}
AIC(child_brow_emo)
AIC(child_brow_emo_bin)
AIC(child_brow_emo_bin_interaction)
```

```{r}
anova(child_brow_emo, child_brow_emo_bin)
```


```{r}
anova(child_brow_emo_bin, child_brow_emo_bin_interaction)
```


#model with just main effects of emotion and bin is the best fit for the data 

```{r}
child_tidy_brow <- tidy(child_brow_emo_bin)

summary(child_brow_emo_bin)
```

#produce table

```{r}
really_nice_table <- dust(child_brow_emo_bin) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```



#now do the same for adults 

```{r}
HA_adult_brow <- df %>%
  filter(emotion %in% c("adult-happy", "adult-angry")) %>%
  filter(muscle == "brow") %>%
  filter(model == "adult") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(HA_adult_brow)

```

#transform to correct normality

```{r}
HA_adult_brow <- HA_adult_brow %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))
```


##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion 
```{r}
adult_brow_emo <- lmer(log_modulus ~ emotion + (1|pp_no), data = HA_adult_brow, REML = FALSE)

beep(1)

```


#main effect for emotion and bin 
```{r}
adult_brow_emo_bin <- lmer(log_modulus ~ emotion + bin + (1|pp_no), data = HA_adult_brow, REML = FALSE)

beep(1)
```

#main effect for emotion and bin and slope for emotion 
```{r}
adult_brow_emo_binS <- lmer(log_modulus ~ emotion + bin + (1 + emotion|pp_no), data = HA_adult_brow, REML = FALSE)

beep(1)
```

#main effect for emotion and bin and emotion*bin interaction and slope for emotion 
```{r}
adult_brow_emo_bin_interaction <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 + emotion|pp_no), data = HA_adult_brow, REML = FALSE)

beep(1)
```

```{r}
AIC(adult_brow_emo)
AIC(adult_brow_emo_bin)
AIC(adult_brow_emo_binS)
AIC(adult_brow_emo_bin_interaction)
```

```{r}
anova(adult_brow_emo, adult_brow_emo_bin)
```
```{r}
anova(adult_brow_emo, adult_brow_emo_binS)
```

```{r}
anova(adult_brow_emo_binS, adult_brow_emo_bin_interaction)
```

#the model with main effect of emotion and bin and slope for emotion was the best fit for the data 

```{r}
adult_tidy_brow <- tidy(adult_brow_emo_binS)
```



```{r}
really_nice_table <- dust(adult_brow_emo_bin) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```

