---
title: "8c_cheek_SF"
output: html_document
---

#load packages
```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(pixiedust)
library(beepr)
```

#read in data 
```{r}
df <- read_csv(here("rileyraw_data", "adult_child_combined", "zdiff_binscreened.csv"))

df$emotion <- as.factor(df$emotion)

df <- df %>% mutate_if(is.character, as.factor)

glimpse(df)

```


SAD-FEAR

#CHEEK-CHILD

#Make df with just sad/fear child face for cheek

```{r}
SF_child_cheek <- df %>%
  filter(emotion %in% c("child-sad", "child-fear")) %>%
  filter(muscle == "cheek") %>%
  filter(model == "child") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(SF_child_cheek)
```

#transform to correct normality

```{r}
SF_child_cheek <- SF_child_cheek %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))

```


##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion and slope for emotion 
```{r}
child_cheek_emo <- lmer(log_modulus ~ emotion + (1 + emotion|pp_no), data = SF_child_cheek, REML = FALSE)

beep(1)

```

#just main effect of emotion and bin, and slope for emotion 
```{r}
child_cheek_emo_bin <- lmer(log_modulus ~ emotion + bin + (1 + emotion|pp_no), data = SF_child_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion and bin and emotion*bin, and slope for emotion (slope for bin doesnt converge)

```{r}
child_cheek_emo_bin_interaction <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 + emotion|pp_no), data = SF_child_cheek, REML = FALSE)

beep(1)
```


```{r}
AIC(child_cheek_emo)
AIC(child_cheek_emo_bin)
AIC(child_cheek_emo_bin_interaction)
```

```{r}
anova(child_cheek_emo, child_cheek_emo_bin)
```


```{r}
anova(child_cheek_emo_bin, child_cheek_emo_bin_interaction)
```

#the model that fits the data the best includes a main effect for emotion and bin and a slope for emotion 

```{r}
child_tidy_cheek <- tidy(child_cheek_emo_bin)
```


```{r}
really_nice_table <- dust(child_cheek_emo_bin) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```




SAD-FEAR

#CHEEK-ADULT

#Make df with just sad/fear Adult face for cheek

```{r}
SF_adult_cheek <- df %>%
  filter(emotion %in% c("adult-sad", "adult-fear")) %>%
  filter(muscle == "cheek") %>%
  filter(model == "adult") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(SF_adult_cheek)
```

#transform to correct normality

```{r}
SF_adult_cheek <- SF_adult_cheek %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))

```


##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion 
```{r}
adult_cheek_emo <- lmer(log_modulus ~ emotion + (1|pp_no), data = SF_adult_cheek, REML = FALSE)

beep(1)

```

#just main effect of emotion and bin
```{r}
adult_cheek_emo_bin <- lmer(log_modulus ~ emotion + bin + (1|pp_no), data = SF_adult_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion and bin and emotion*bin

```{r}
adult_cheek_emo_bin_interaction <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 |pp_no), data = SF_adult_cheek, REML = FALSE)

beep(1)
```

#note: adding bin or emotion as a slope makes the model fail to converge 



```{r}
AIC(adult_cheek_emo)
AIC(adult_cheek_emo_bin)
AIC(adult_cheek_emo_bin_interaction)
```

```{r}
anova(adult_cheek_emo, adult_cheek_emo_bin)
```


```{r}
anova(adult_cheek_emo_bin, adult_cheek_emo_bin_interaction)
```

#the model that fits the data the best includes a main effect for emotion and bin and emotion*bin interaction 

```{r}
adult_tidy_cheek <- tidy(adult_cheek_emo_bin_interaction)
```

#really nice table

```{r}
really_nice_table <- dust(adult_cheek_emo_bin_interaction) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table

```



