---
title: "8d_brow_SF"
output: html_document
---

#load packages
```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(pixiedust)
library(beepr)
```

#read in data 
```{r}
df <- read_csv(here("rileyraw_data", "adult_child_combined", "zdiff_binscreened.csv"))

df$emotion <- as.factor(df$emotion)

df <- df %>% mutate_if(is.character, as.factor)

glimpse(df)

```


SAD-FEAR

#BROW-CHILD

#Make df with just sad/fear child face for brow

```{r}
SF_child_brow <- df %>%
  filter(emotion %in% c("child-sad", "child-fear")) %>%
  filter(muscle == "brow") %>%
  filter(model == "child") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(SF_child_brow)
```

#transform to correct normality

```{r}
SF_child_brow <- SF_child_brow %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))

```


##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion and slope for emotion 
```{r}
child_brow_emo2 <- lmer(log_modulus ~ emotion + (1 + emotion|pp_no), data = SF_child_brow, REML = FALSE)

beep(1)

```

#just main effect of emotion and bin, and slope for emotion 
```{r}
child_brow_emo_bin2 <- lmer(log_modulus ~ emotion + bin + (1 + emotion|pp_no), data = SF_child_brow, REML = FALSE)

beep(1)
```

#main effect of emotion and bin and emotion*bin, and slope for emotion (slope for bin doesnt converge)

```{r}
child_brow_emo_bin_interaction2 <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 + emotion|pp_no), data = SF_child_brow, REML = FALSE)

beep(1)
```


```{r}
AIC(child_brow_emo2)
AIC(child_brow_emo_bin2)
AIC(child_brow_emo_bin_interaction2)
```

```{r}
anova(child_brow_emo2, child_brow_emo_bin2)
```


```{r}
anova(child_brow_emo_bin2, child_brow_emo_bin_interaction2)
```

#BEST FIT
#the model that fits the data the best includes a main effect for emotion and a slope for emotion 

```{r}
child_tidy_brow2 <- tidy(child_brow_emo2)
```

#really nice table
```{r}
really_nice_table <- dust(child_brow_emo2) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```


#BROW-ADULT


#Make df with just sad/fear adult face for brow

```{r}
SF_adult_brow <- df %>%
  filter(emotion %in% c("adult-sad", "adult-fear")) %>%
  filter(muscle == "brow") %>%
  filter(model == "adult") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(SF_adult_brow)
```

#transform to correct normality

```{r}
SF_adult_brow <- SF_adult_brow %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))

```


##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion and slope for emotion 
```{r}
adult_brow_emo2 <- lmer(log_modulus ~ emotion + (1 + emotion|pp_no), data = SF_adult_brow, REML = FALSE)

beep(1)

```

#just main effect of emotion and bin, and slope for emotion 
```{r}
adult_brow_emo_bin2 <- lmer(log_modulus ~ emotion + bin + (1 + emotion|pp_no), data = SF_adult_brow, REML = FALSE)

beep(1)
```

#main effect of emotion and bin and emotion*bin, and slope for emotion (slope for bin doesnt converge)

```{r}
adult_brow_emo_bin_interaction2 <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 + emotion|pp_no), data = SF_adult_brow, REML = FALSE)

beep(1)
```


```{r}
AIC(adult_brow_emo2)
AIC(adult_brow_emo_bin2)
AIC(adult_brow_emo_bin_interaction2)
```

```{r}
anova(adult_brow_emo2, adult_brow_emo_bin2)
```


```{r}
anova(adult_brow_emo_bin2, adult_brow_emo_bin_interaction2)
```

#BEST FIT
#the model that fits the data the best includes a main effect for emotion and a slope for emotion 

```{r}
adult_tidy_brow2 <- tidy(adult_brow_emo2)
```

#really nice table
```{r}
really_nice_table <- dust(adult_brow_emo2) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table


```


#ALL_EMO-CHILD

BROW

#Make df with just child face for brow

```{r}
child_brow <- df %>%
  filter(muscle == "brow") %>%
  filter(model == "child") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(child_brow)
```

#transform to correct normality

```{r}
child_brow <- child_brow %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))

```


##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion 
```{r}
child_brow_emo4 <- lmer(log_modulus ~ emotion + (1|pp_no), data = child_brow, REML = FALSE)

beep(1)

```

#just main effect of emotion and bin, and slope for emotion 
```{r}
child_brow_emo_bin4 <- lmer(log_modulus ~ emotion + bin + (1 + emotion|pp_no), data = child_brow, REML = FALSE)

beep(1)
```

#main effect of emotion and bin and emotion*bin, and slope for emotion (slope for bin doesnt converge)

```{r}
child_brow_emo_bin_interaction4 <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 + emotion|pp_no), data = child_brow, REML = FALSE)

beep(1)
```


```{r}
AIC(child_brow_emo4)
AIC(child_brow_emo_bin4)
AIC(child_brow_emo_bin_interaction4)
```

```{r}
anova(child_brow_emo4, child_brow_emo_bin4)
```


```{r}
anova(child_brow_emo_bin4, child_brow_emo_bin_interaction4)
```

#BEST FIT
#the model that fits the data the best includes a main effect for emotion and bin and a slope for emotion 

```{r}
child_tidy_brow4 <- tidy(child_brow_emo_bin4)
```

#really nice table 

```{r}
really_nice_table <- dust(child_brow_emo_bin4) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```

#ALL_EMO_ADULT

BROW

#Make df with just adult face for brow

```{r}
adult_brow <- df %>%
  filter(muscle == "brow") %>%
  filter(model == "adult") %>%
  arrange(pp_no, emotion, trial, bin)

glimpse(adult_brow)
```

#transform to correct normality

```{r}
adult_brow <- adult_brow %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))

```


##Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, then bin and then bin*emotion

###just main effect of emotion and slope for emotion
```{r}
adult_brow_emo4 <- lmer(log_modulus ~ emotion + (1 + emotion|pp_no), data = adult_brow, REML = FALSE)

beep(1)

```

#just main effect of emotion and bin, and slope for emotion 
```{r}
adult_brow_emo_bin4 <- lmer(log_modulus ~ emotion + bin + (1 + emotion|pp_no), data = adult_brow, REML = FALSE)

beep(1)
```

#main effect of emotion and bin and emotion*bin, and slope for emotion (slope for bin doesnt converge)

```{r}
adult_brow_emo_bin_interaction4 <- lmer(log_modulus ~ emotion + bin + emotion*bin + (1 + emotion|pp_no), data = adult_brow, REML = FALSE)

beep(1)
```


```{r}
AIC(adult_brow_emo4)
AIC(adult_brow_emo_bin4)
AIC(adult_brow_emo_bin_interaction4)
```

```{r}
anova(adult_brow_emo4, adult_brow_emo_bin4)
```

```{r}
anova(adult_brow_emo_bin4, adult_brow_emo_bin_interaction4)
```


#BEST FIT

#The model that fits the data the best is one with a main effect of emotion and slope for emotion


```{r}
adult_tidy_brow4 <- tidy(adult_brow_emo4)
```


#really nice table 
```{r}
really_nice_table <- dust(adult_brow_emo4) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```









