---
title: "basline_test"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


# Load packages
```{r}
library(tidyverse)
library(here)
library(naniar)
library(ggbeeswarm)
library(ggeasy)
```

# Read in clean data

Using map to read in and bind together many csv files- notes from this blog post using option2A www.jenrichmond.rbind.io/post/use-map-to-read-many-csv-files

### read child files
```{r message=FALSE, warning=FALSE}
data_path1 <- here("clean_data", "clean_data_childface")

files <- dir(data_path1, pattern = "*.xlsx.csv")

child_data <- files %>%
  map(~ read_csv(file.path(data_path1, .))) %>%
  reduce(rbind)
```

### read adult files
```{r message=FALSE, warning=FALSE}
data_path2 <- here("clean_data", "clean_data_adultface")

files <- dir(data_path2, pattern = "*.xlsx.csv")

adult_data <- files %>%
  map(~ read_csv(file.path(data_path2, .))) %>%
  reduce(rbind)
```

# create participant and condition columns out of filename

NOTE working with adults data here because it isn't missing data--- you will need to replicate with child

Use separate() to split the filename into  pp_no and condition and mutate with str_sub to drop the last 6 characters off the end of the values in the condition column to get rid of the .xlsx

```{r}

adult_cond <- adult_data %>%
  separate(file_name, into = c("pp_no", "model", "emotion"), sep = "_") %>% 
  mutate(emotion = str_sub(emotion, end = -6)) 
```

```{r}
# bind child_cond and adult_cond together using rbind

# then use write_csv to get a new csv that contains all the clean data
```

-------------
```{r}
library(tidyverse)
```

```{r}
clean_data <- read_csv()

```

# Q1 are there baseline differences between brow and cheek?

1. Filter the data to only include bin 0 (baseline- BL) and plot BL scores for each trial, separately for brow and cheek, coloured by positive/negative. 

```{r}
adult_BL <- adult_cond %>%
  filter(bin == "bin_0")
```

#filter out data for participant 404, group by model, muscle, emotion
```{r}
pp404_BL <- adult_BL[193:256,] %>%
  group_by(model, muscle, emotion) %>%
  summarise(meanRMS = mean(rms), sdRMS = sd(rms))

```

#make a new outlier variable
if sdRMS > 2 = TRUE, if not = FALSE
```{r}
pp404_BL_Out <- pp404_BL %>%
  mutate(outlier = if_else(sdRMS > (meanRMS + 2*sdRMS), "TRUE", "FALSE"))


```

#testing it on the rest of the baseline adult face data

```{r}

adult_BL_stats <- adult_BL %>%
  group_by(pp_no, model, muscle, emotion) %>%
  mutate(meanRMS = mean(rms), sdRMS = sd(rms))

adult_BL_outlier <- adult_BL_stats %>%
  mutate(outlier = if_else(rms > (meanRMS + 2*sdRMS), "TRUE", "FALSE"))
  
```

#Test Child data

#arrange columns

```{r}
child_cond <- child_data %>%
  separate(file_name, into = c("pp_no", "model", "emotion"), sep = "_") %>% 
  mutate(emotion = str_sub(emotion, end = -6)) 
```


#use the filter function to obtain only baseline data 
```{r}
child_BL <- child_cond %>%
  filter(bin == "bin_0")

```

#create new columns for mean and std 
```{r}
child_BL_stats <- child_BL %>%
  group_by(pp_no, model, muscle, emotion) %>%
  mutate(meanRMS = mean(rms), sdRMS = sd(rms))
 

```

#create a new column with information about outlier 
```{r}

child_BL_outlier <- child_BL_stats %>%
  mutate(outlier = if_else(rms > (meanRMS + 2*sdRMS), "TRUE", "FALSE"))


```


```{r}
child_BL_outlier_sum <- child_BL_outlier %>%
  filter(outlier == "TRUE")
  
  
```

#check if outlier is logical 

```{r}
glimpse(child_BL_outlier)
```

#make outliter logical for child and adult face data

```{r}
child_BL_outlier$outlier <- as.logical(child_BL_outlier$outlier)

adult_BL_outlier$outlier <- as.logical(adult_BL_outlier$outlier)
```

#make logical variable code as 1 = true, 0 = false, so they are able to be summed for adult and child face data

```{r}
out_count_child <- child_BL_outlier %>%
  group_by(pp_no, model, emotion, muscle) %>%
  summarise(out_count = sum(outlier), trial_count = n())


out_count_adult <- adult_BL_outlier %>%
  group_by(pp_no, model, emotion, muscle) %>%
  summarise(out_count = sum(outlier), trial_count = n())
```

#plot outliers for child face condition 

```{r}
child_BL_outlier %>%
  filter(emotion == "121") %>%
  ggplot(aes(x = trial, y = rms, colour = outlier)) +
  geom_quasirandom() +
  facet_wrap(~ muscle) +
  labs(title = "condition child_121")


child_BL_outlier %>%
  filter(emotion == "323") %>%
  ggplot(aes(x = trial, y = rms, colour = outlier)) +
  geom_quasirandom() +
  facet_wrap(~ muscle) +
  labs(title = "condition child_323")



child_BL_outlier %>%
  filter(emotion == "424") %>%
  ggplot(aes(x = trial, y = rms, colour = outlier)) +
  geom_quasirandom() +
  facet_wrap(~ muscle) +
  labs(title = "condition child_424")



child_BL_outlier %>%
  filter(emotion == "525") %>%
  ggplot(aes(x = trial, y = rms, colour = outlier)) +
  geom_quasirandom() +
  facet_wrap(~ muscle) +
  labs(title = "condition child_525")
```

#plot outliers for adult face condition 
```{r}

adult_BL_outlier %>%
  filter(emotion == "131") %>%
  ggplot(aes(x = trial, y = rms, colour = outlier)) +
  geom_quasirandom() +
  facet_wrap(~ muscle) +
  labs(title = "condition adult_131")

adult_BL_outlier %>%
  filter(emotion == "232") %>%
  ggplot(aes(x = trial, y = rms, colour = outlier)) +
  geom_quasirandom() +
  facet_wrap(~ muscle) +
  labs(title = "condition adult_232")

adult_BL_outlier %>%
  filter(emotion == "434") %>%
  ggplot(aes(x = trial, y = rms, colour = outlier)) +
  geom_quasirandom() +
  facet_wrap(~ muscle) +
  labs(title = "condition adult_434")

adult_BL_outlier %>%
  filter(emotion == "535") %>%
  ggplot(aes(x = trial, y = rms, colour = outlier)) +
  geom_quasirandom() +
  facet_wrap(~ muscle) +
  labs(title = "condition adult_535")
```

