---
title: "next steps clean data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r}
library(tidyverse)
library(here)
library(naniar)
library(ggbeeswarm)
library(ggeasy)

```

# Read in clean data

Questions for Sahar - why are there 8 variables for faces and 6 for non?

```{r}

faces <- read_csv(here("data", "clean_data", "faces_clean.csv"))

non <- read_csv(here("data", "clean_data", "non-faces_clean.csv"))

```

# use naniar to look at missing data


```{r}
naniar::vis_miss(faces)

naniar::vis_miss(non)

```

# create participant and condition columns out of filename

NOTE working with nonface here because it isn't missing data--- you will need to replicate with both face and non face

Use separate() to split the filename into pp_no and condition and mutate with str_sub to drop the last 6 characters off the end of the values in the condition column to get rid of the .xlsx

```{r}

non_cond <- non %>%
  separate(file_name, into = c("pp_no", "condition"), sep = "_") %>% 
  mutate(condition = str_sub(condition, end = -6)) 
```


# Q1 are there baseline differences between brow and cheek?

1. Filter the data to only include bin 0 (baseline- BL) and plot BL scores for each trial, separately for brow and cheek, coloured by positive/negative. 

```{r}
non_BL <- non_cond %>%
  filter(bin == "bin_0")
```

Plot baseline 

```{r}
non_BL %>%
  ggplot(aes(x = trial , y = rms, colour = condition)) +
  geom_quasirandom() + 
  facet_wrap(~ muscle)
```

```{r}
non_BL %>%
  group_by(muscle, trial)  %>%
  summarise(meanRMS = mean(rms), sdRMS = sd(rms))
```

Next challenge to work out- identify trials that need to be excluded because the baseline score is more than 2SD above the mean for that participant?? 

work out for each participant for every one of these baseline scores is it more than 2SD above 

what is the mean baseline score across trials for the brow and cheek for each kid for each condition - are there any values within the scores that are contributing to the mean above the mean for that kid for that condition for that muscle 

group by participant, condition and muscle 
mutate - outlier - FALSE and TRUE according to condition 
make a tiny data frame to solve it 