---
title: "calculate_z-score_test"
author: "Sahar Fatima"
date: "16/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Objective: 
testing to see if calculating z-scores with BL and bins separately makes a difference

### load packages 
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(formattable) # useful for controlling decimal places
library(here)
library(papaja)

options(scipen = 999) #set no scientific notation
```

### The process
- first, make data wide using pivot_wider so that brow and cheek are in columns
- use scale() to transform RMS scores into z scores for each participant.
- then make bin wide so that each row represents a single trial and bins 1-10 are in different columns
- make new column for each bin, calculating the difference between that binZ and baselineZ.

# Calculating 
Normally, to center a variable, you would subtract the mean of all data points from each individual data point. With scale(), this can be accomplished in one simple call.

center variable A using the scale() function
`scale(A, center = TRUE, scale = FALSE)`

### 2. Generating Z-Scores

generate z-scores for variable A using the scale() function
`scale(A, center = TRUE, scale = TRUE)`

## read in data 

```{r message=FALSE, warning=FALSE}
face <- read_csv(here("R_analysing", "data", "7_face_false.csv")) %>% # face data 
  select(-outlier1.5SD)

non<- read_csv(here("R_analysing", "data", "7_non_false.csv")) %>% # non-face data
  select(-outlier1.5SD)
```


### going to try calculating z-score on baseline and bin separately.
Face First
```{r}
# make BL data frame
face_BL <- face %>%
  filter(bin_no == 0) %>%
  pivot_wider(names_from = muscle, 
              values_from = rms) %>%
  group_by(pp_no) %>%
  mutate(Zbrow = scale(brow, center = TRUE, scale = TRUE)) %>%
  mutate(Zcheek = scale(cheek, center = TRUE, scale = TRUE))

faces_bin <- face %>%
  filter(bin_no != 0) %>%
  pivot_wider(names_from = muscle, 
              values_from = rms) %>%
  group_by(pp_no) %>%
  mutate(Zbrow = scale(brow, center = TRUE, scale = TRUE)) %>%
  mutate(Zcheek = scale(cheek, center = TRUE, scale = TRUE))

zface <- rbind(face_BL, faces_bin) %>%
  arrange(pp_no, condition, trial, bin)

summary(zface)
```


Now non-face
```{r}
# make BL data frame
non_BL <- non %>%
  filter(bin_no == 0) %>%
  pivot_wider(names_from = muscle, 
              values_from = rms) %>%
  group_by(pp_no) %>%
  mutate(Zbrow = scale(brow, center = TRUE, scale = TRUE)) %>%
  mutate(Zcheek = scale(cheek, center = TRUE, scale = TRUE))

non_bin <- non %>%
  filter(bin_no != 0) %>%
  pivot_wider(names_from = muscle, 
              values_from = rms) %>%
  group_by(pp_no) %>%
  mutate(Zbrow = scale(brow, center = TRUE, scale = TRUE)) %>%
  mutate(Zcheek = scale(cheek, center = TRUE, scale = TRUE))

znon <- rbind(non_BL, non_bin) %>%
  arrange(pp_no, condition, trial, bin)

summary(znon)
```


## facial stimuli 
### faces cheek now
```{r}
# add a muscle column to make things easier to join back together later
zface_cheek <- zface %>%
  mutate(muscle = "cheek") %>%
  select(pp_no, condition, bin, trial, muscle, Zcheek) 

# Make the bin column wide and rename bin_0 as BL (i.e. baseline)
zface_cheek_wide <- zface_cheek %>%
  pivot_wider(names_from = bin, 
              values_from = Zcheek) %>%
  rename(BL = bin_0)

# mutate() diff scores - Use wide columns to calcuate the difference between each bin column and BL, creating a new set of columns starting with “diff”, drop BL column and all columns starting with bin (i.e. raw z scores).

# note - This df contains for each bin the difference between stimulus and basline, so POSITIVE difference scores = greater activity during STIM than BL and NEGATIVE difference scores = greater activity during BL than STIM

zface_cheek_diff <- zface_cheek_wide %>% 
  mutate(diff_bin1 = bin_1 - BL, 
         diff_bin2 = bin_2 - BL,
         diff_bin3 = bin_3- BL, 
         diff_bin4 = bin_4 - BL,
         diff_bin5 = bin_5 - BL, 
         diff_bin6 = bin_6 - BL,
         diff_bin7 = bin_7 - BL, 
         diff_bin8 = bin_8 - BL, 
         diff_bin9 = bin_9 - BL, 
         diff_bin10 = bin_10 - BL) %>%
  select(-BL, - starts_with("bin"))

# going to make it long now 
zface_cheek_long <- zface_cheek_diff %>%
  pivot_longer(names_to = "bin", 
               values_to = "Zdiff", 
               diff_bin1:diff_bin10)
```

#### Plotting face_cheek
```{r}
zface_cheek_long$condition <- as.factor(zface_cheek_long$condition)

zface_cheek_long$bin <- fct_relevel(zface_cheek_long$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

zface_cheek_long %>%
  group_by(condition, bin) %>%
  summarise(meancheekdiff = mean(Zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meancheekdiff, colour = condition, group = condition)) +
  geom_point() + 
  geom_line() +
  labs(title = "cheek activity difference from baseline in response to faces") +
  scale_y_continuous(limits = c(-0.2, 0.3))
```

### faces - brow
```{r}
# add a muscle column to make things easier to join back together later
zface_brow <- zface %>%
  mutate(muscle = "brow") %>%
  select(pp_no, condition, bin, trial, muscle, Zbrow) 

# Make the bin column wide and rename bin_0 as BL (i.e. baseline)
zface_brow_wide <- zface_brow %>%
  pivot_wider(names_from = bin, 
              values_from = Zbrow) %>%
  rename(BL = bin_0)

# mutate() diff scores - Use wide columns to calcuate the difference between each bin column and BL, creating a new set of columns starting with “diff”, drop BL column and all columns starting with bin (i.e. raw z scores).

# note - This df contains for each bin the difference between stimulus and basline, so POSITIVE difference scores = greater activity during STIM than BL and NEGATIVE difference scores = greater activity during BL than STIM

zface_brow_diff <- zface_brow_wide %>% 
  mutate(diff_bin1 = bin_1 - BL, 
         diff_bin2 = bin_2 - BL,
         diff_bin3 = bin_3- BL, 
         diff_bin4 = bin_4 - BL,
         diff_bin5 = bin_5 - BL, 
         diff_bin6 = bin_6 - BL,
         diff_bin7 = bin_7 - BL, 
         diff_bin8 = bin_8 - BL, 
         diff_bin9 = bin_9 - BL, 
         diff_bin10 = bin_10 - BL) %>%
  select(-BL, - starts_with("bin"))

# going to make it long now 
zface_brow_long <- zface_brow_diff %>%
  pivot_longer(names_to = "bin", 
               values_to = "Zdiff", 
               diff_bin1:diff_bin10)
  

```


```{r}
zface_full <- bind_rows(zface_brow_long, zface_cheek_long) %>%
  arrange(pp_no, condition, trial, muscle, bin)
```



