---
title: "lmm_analyses_2x500ms_bins"
author: "Sahar Fatima"
date: "14/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## load packages 

```{r message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggeffects)
library(broom.mixed)
library(pixiedust)
library(beepr)
library(effsize)
library(lsmeans)
library(rockchalk)
library(papaja)
```

## read in data 

```{r message=FALSE, warning=FALSE}
face <- read_csv(here("R_analysing", "data", "9_face_zdiff_screened.csv")) %>%
  mutate(condition = recode(condition, "429" = "angry","673" = "happy", .default = "NA"))

non <- read_csv(here("R_analysing", "data", "9_non_zdiff_screened.csv")) %>%
  mutate(condition = recode(condition, "913" = "negative","285" = "positive", .default = "NA"))
```

## fix data types 

```{r}
face$condition <- as.factor(face$condition)

face <- face %>% 
  mutate_if(is.character,as.factor) 

levels(face$bin)

face$bin <- fct_relevel(face$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

non$condition <- as.factor(non$condition)

non <- non %>% 
  mutate_if(is.character,as.factor)

non$bin <- fct_relevel(non$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

```

## splitting data into 2 500ms bins (rather than 10 100ms bins)
Going to try to use combine levels: https://rdrr.io/cran/rockchalk/man/combineLevels.html from rockchalk package
^ couldn't figure it out - just going to use recode?
```{r}
face <- face %>%
  mutate(bin = recode(bin, "diff_bin1" = "bin1", "diff_bin2" = "bin1", "diff_bin3" = "bin1", "diff_bin4" = "bin1", "diff_bin5" = "bin1", "diff_bin6" = "bin2", "diff_bin7" = "bin2", "diff_bin8" = "bin2", "diff_bin9" = "bin2", "diff_bin10" = "bin2"))

levels(face$bin)

non <- non %>%
  mutate(bin = recode(bin, "diff_bin1" = "bin1", "diff_bin2" = "bin1", "diff_bin3" = "bin1", "diff_bin4" = "bin1", "diff_bin5" = "bin1", "diff_bin6" = "bin2", "diff_bin7" = "bin2", "diff_bin8" = "bin2", "diff_bin9" = "bin2", "diff_bin10" = "bin2"))

glimpse(face)
```

## make cheek and brow data frames
```{r}
#face_cheek 
face_cheek <- face %>%
  filter(muscle == "cheek") %>%
  arrange(pp_no, condition, trial, bin)

#face_brow
face_brow <- face %>%
  filter(muscle == "brow") %>%
  arrange(pp_no, condition, trial, bin)

#non_cheek 
non_cheek <- non %>%
  filter(muscle == "cheek") %>%
  arrange(pp_no, condition, trial, bin)

#non_brow
non_brow <- non %>%
  filter(muscle == "brow") %>%
  arrange(pp_no, condition, trial, bin)

```

# FACE CHEEK
## plot cheek responding to facial stimuli 

```{r}
face_cheek_plot <- face_cheek %>%
  filter(muscle == "cheek") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    # Thinner lines
                    width=.2) + 
  theme_minimal()

face_cheek_plot
```

## do lmm face_cheek
```{r}
face_cheek <- face_cheek %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))

lm_face_cheek <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition|pp_no), data = face_cheek, REML = FALSE)

anova(lm_face_cheek)
summary(lm_face_cheek)
```

# FACE BROW
## plot brow responding to faces

```{r}
face_brow_plot <- face_brow %>%
  filter(muscle == "brow") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    # Thinner lines
                    width=.2) + 
  theme_apa(box = TRUE)

face_brow_plot
```

## lmm_face_brow
```{r}
face_brow <- face_brow %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))

lm_face_brow <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition + bin|pp_no), data = face_brow, REML = FALSE)


anova(lm_face_brow)

summary(lm_face_brow)

```

# NON-FACE BROW
```{r}
non_brow <- non_brow %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))

lm_non_brow <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition|pp_no), data = non_brow, REML = FALSE)

anova(lm_non_brow)
```

# NON-FACE CHEEK

## plot 
```{r}
non_cheek %>%
  filter(muscle == "cheek") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    # Thinner lines
                    width=.2) + 
  theme_apa(box = TRUE)
```


## lmm_non_cheek
```{r}
non_cheek <- non_cheek %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))

lm_non_cheek <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition|pp_no), data = non_cheek, REML = FALSE)

anova(lm_non_cheek)
```

