---
title: "child-adult"
output: html_document
---

#load packages
```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(pixiedust)
library(beepr)
```

#read in data 
```{r}
df <- read_csv(here("rileyraw_data", "adult_child_combined", "zdiff_binscreened.csv"))

df$emotion <- as.factor(df$emotion)

df <- df %>% mutate_if(is.character, as.factor)

glimpse(df)
```

#make df with just happy and angry and cheek muscle 

```{r}
HA_cheek <- df %>%
  filter(emotion %in% c("happy", "angry")) %>%
  filter(muscle == "cheek") %>%
  arrange(pp_no, model, emotion, trial, bin)

glimpse(HA_cheek)
```

#trasnform to correct normality 
```{r}
HA_cheek <- HA_cheek %>%
  mutate(log_modulus = sign(zdiff) + log(1+abs(zdiff)))
```


#Likelihood Ratio Tests

##what would the model fit look like if we added main effects of emotion, and then mode, and then bin and then bin*emotion and bin*emotion*model

###just main effect of emotion and slope for emotion 
```{r}
cheek_emo <- lmer(log_modulus ~ emotion + (1 + emotion|pp_no), data = HA_cheek, REML = FALSE)

beep(1)
```

#main effect for emotion and model and slope for emotion 

```{r}
cheek_emo_model <- lmer(log_modulus ~ emotion + model + (1 + emotion|pp_no), data = HA_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion, model and bin and slope for emotion 
```{r}
cheek_emo_model_bin <- lmer(log_modulus ~ emotion + model + bin + (1 + emotion|pp_no), data = HA_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion, model and bin and slope for emotion and model
```{r}
cheek_emo_model_binS <- lmer(log_modulus ~ emotion + model + bin + (1 + emotion + model|pp_no), data = HA_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion and model and bin and emotion*model, and slope for emotion and model
```{r}
cheek_emo_model_binS2 <- lmer(log_modulus ~ emotion + model + bin + emotion*model + (1 + emotion + model|pp_no), data = HA_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion and model and bin and emotion*model and emotion*bin, and slope for emotion and model (FAILS TO CONVERGE)
```{r}
cheek_emo_model_binS3 <- lmer(log_modulus ~ emotion + model + bin + emotion*model + emotion*bin + (1 + emotion + model|pp_no), data = HA_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion and model and bin and emotion*model and bin*model, and slope for emotion and model (FAILS TO CONVERGE)
```{r}
cheek_emo_model_binS4 <- lmer(log_modulus ~ emotion + model + bin + emotion*model + model*bin + (1 + emotion + model|pp_no), data = HA_cheek, REML = FALSE)

beep(1)
```

#main effect of emotion and model and bin and emotion*model and emotion*model*bin, and slope for emotion and model (FAILS TO CONVERGE)
```{r}
cheek_emo_model_binS5 <- lmer(log_modulus ~ emotion + model + bin + emotion*model + model*bin*emotion + (1 + emotion + model|pp_no), data = HA_cheek, REML = FALSE)

beep(1)
```


#main effect of emotion and model and bin and emotion*model and emotion*model*bin, and slope for emotion and model and emotion*model
```{r}
cheek_emo_model_binS5 <- lmer(log_modulus ~ emotion + model + bin + emotion*model + model*bin*emotion + (1 + emotion + model + emotion*model|pp_no), data = HA_cheek, REML = FALSE)

beep(1)
```

```{r}
AIC(cheek_emo)
AIC(cheek_emo_model)
AIC(cheek_emo_model_bin)
AIC(cheek_emo_model_binS)
AIC(cheek_emo_model_binS2)
AIC(cheek_emo_model_binS5)

```

```{r}
anova(cheek_emo,cheek_emo_model)
```


```{r}
anova(cheek_emo_model, cheek_emo_model_bin)
```


```{r}
anova(cheek_emo_model_bin, cheek_emo_model_binS)
```


```{r}
anova(cheek_emo_model_binS, cheek_emo_model_binS2)
```


```{r}
anova(cheek_emo_model_binS2, cheek_emo_model_binS3)
```



```{r}
anova(cheek_emo_model_binS3, cheek_emo_model_binS4)

```

```{r}
anova(cheek_emo_model_binS4, cheek_emo_model_binS5)
```

#BEST FIT 
##model that fits the data the best includes main effect of emotion and model and bin and emotion*model and emotion*model*bin, and slope for emotion and model and emotion*model

#really nice table 
```{r}
really_nice_table <- dust(cheek_emo_model_binS5) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```















