---
title: "next steps clean data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r}
library(tidyverse)
library(here)
library(naniar)
library(ggbeeswarm)
library(ggeasy)
```

# Read in clean data

Using map to read in and bind together many csv files- notes from this blog post using option2A www.jenrichmond.rbind.io/post/use-map-to-read-many-csv-files

### read child files
```{r message=FALSE, warning=FALSE}
data_path1 <- here("rileyraw_data", "clean_data_childface")

files <- dir(data_path1, pattern = "*.xlsx.csv")

child_data <- files %>%
  map(~ read_csv(file.path(data_path1, .))) %>%
  reduce(rbind)
```

### read adult files
```{r message=FALSE, warning=FALSE}
data_path2 <- here("rileyraw_data", "clean_data_adultface")

files <- dir(data_path2, pattern = "*.xlsx.csv")

adult_data <- files %>%
  map(~ read_csv(file.path(data_path2, .))) %>%
  reduce(rbind)
```


# use naniar to look at missing data
 
Check on missing values child data- are the NA? or totally missing??

```{r}
naniar::vis_miss(child_data)

naniar::vis_miss(adult_data)

```

# create participant and condition columns out of filename

NOTE working with adults data here because it isn't missing data--- you will need to replicate with child

Use separate() to split the filename into  pp_no and condition and mutate with str_sub to drop the last 6 characters off the end of the values in the condition column to get rid of the .xlsx

```{r}

adult_cond <- adult_data %>%
  separate(file_name, into = c("pp_no", "model", "emotion"), sep = "_") %>% 
  mutate(emotion = str_sub(emotion, end = -6)) 
```


# Q1 are there baseline differences between brow and cheek?

1. Filter the data to only include bin 0 (baseline- BL) and plot BL scores for each trial, separately for brow and cheek, coloured by positive/negative. 

```{r}
adult_BL <- adult_cond %>%
  filter(bin == "bin_0")
```

Plot baseline 

```{r}
adult_BL %>%
  ggplot(aes(x = trial , y = rms, colour = emotion)) +
  geom_quasirandom() +
  facet_wrap(~ muscle)
```

```{r}
adult_BL %>%
  group_by(muscle, emotion)  %>%
  summarise(meanRMS = mean(rms), sdRMS = sd(rms))
```

Next challenge to work out- identify trials that need to be excluded because the baseline score is more than 2SD above the mean for that participant?? 

