---
title: "SFLinR-LMM example"
author: "Jen Richmond"
date: "09/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)

set.seed(666)
```

# generate participant and item identifiers

gl is generate levels, generate 6 levels and repeat them 20 times
```{r}
ppt_ids <- gl(6,20)


```

# generate item identifers

generate 20 levels and repeat them once
```{r}
it_ids <- gl(20,1)
```

All 6 participants responded to all items, so we need to repeat them 6 times. 

```{r}
it_ids <- rep(it_ids, 6)


```

Check both ppt and it ids are 120 obs long.

```{r}
length(ppt_ids) 
length(it_ids) 
```

Make word freq predictpr. Each item needs own log freq value. Use rexp() to get random expotentially distributed numbers

```{r}
logfreqs <- round(rexp(20) * 5, 2)

# repeat 6 times

logfreqs <- rep(logfreqs, 6)

length(logfreqs
       )
```

# put into tibble

```{r}
xdata <- tibble(ppt = ppt_ids, item = it_ids, freq = logfreqs)
```

Add response

```{r}
xdata$int <- 300
```

Varying intercepts per participant?

```{r}
ppt_ints <- rnorm(6, sd = 40)

ppt_ints

```

add varying intercepts to tibble, making sure the intercept is the same for all 20 trials per ppt. 

```{r}
xdata$ppt_ints <- rep(ppt_ints, each = 20)
```

Generate varying item intercepts, repeate 6 times for 6 ppts
```{r}
item_ints <- rnorm(20, sd = 20)


item_ints <- rep(item_ints, times = 6)

length(item_ints)
```

Add to tibble

```{r}
xdata$item_ints <- item_ints
```

Adds errors

```{r}
xdata$error <- rnorm(120, sd = 20)
```

add effect, imagining the slop is -5, each increase in freq of 1, durations decrease by 5ms
```{r}
xdata$effect <- (-5)  * xdata$freq
```

create response variable

```{r}
xdata <- xdata %>% 
  mutate(dur = int + ppt_ints + item_ints + error + effect)
```

dur contains "random" bits ...
- participant varying intercepts (pp_ints) 
- item varying intercepts (int_ints) 
- error

... and systematic bits
- overall intercept (int)
- effect 

The int and effect are fmailiar from linear regression, only difference is now we also allow participant and item spefici variations

# make data look real
drop columns that generated the data

```{r}
xreal <- xdata %>%
  select(-(int:effect))
```

# load packages
```{r}
library(lme4)
```


# build model

Predicting vowel duration from word frequency. Freq is a fixed effect because it is continuous (random can only be categorical) and we expect it to have a systematic effect on duration that would replicate in a different cample. ppt and item are random, because you dont know how they will behave in advance and they might behave in unpredictable (random ways)

This model allows for varying intercepts for participants and items. 

```{r}
xmd1 <- lmer(dur ~ freq + (1|ppt) + (1|item), data = xreal, REML = FALSE)

summary(xmd1)
```

# NOTES and LINKs

https://stats.stackexchange.com/questions/26855/example-reports-for-mixed-model-analysis-using-lmer-in-biology-psychology-and-m


https://www.theanalysisfactor.com/writing-results-mixed-models/

Best practice guide
https://www.sciencedirect.com/science/article/pii/S0749596X20300061

Prose 
https://verbingnouns.github.io/notebooks/prose_statistics.nb.html