---
title: "1_map_extended_data"
author: "Sahar Fatima"
date: "16/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load packages
```{r}
library(readxl)
library(tidyverse)
library(here)
library(janitor)
```

### need to test cleaning on one pp
```{r message=FALSE, warning=FALSE}
# read in data
test <- read_excel(here("extended_cleaning_analysis", "data", "raw_data", "face", "pp481_429.xlsx")) %>%
  mutate_if(is.character,as.double) %>%
  mutate(file_name = "pp604_429.xlsx") 

# remove rows and columns
test_remove <- test[3:23,] %>%
  remove_empty(which = "cols")

# rename variables 
test_rename <- test_remove %>%
  rename(bin = BROW, 
         trial1_brow = BROWDF...2, 
         trial1_cheek = CHEEKDF...3, 
         trial2_brow = BROWDF...7,
         trial2_cheek = CHEEKDF...8, 
         trial3_brow = BROWDF...12, 
         trial3_cheek = CHEEKDF...13, 
         trial4_brow = BROWDF...17, 
         trial4_cheek = CHEEKDF...18,
         trial5_brow = BROWDF...22,
         trial5_cheek = CHEEKDF...23, 
         trial6_brow = BROWDF...27, 
         trial6_cheek = CHEEKDF...28,
         trial7_brow = BROWDF...32, 
         trial7_cheek = CHEEKDF...33, 
         trial8_brow = BROWDF...37, 
         trial8_cheek = CHEEKDF...38)

test_bin <- test_rename %>%
  mutate(bin = c("bin_0", "bin_1", "bin_2", "bin_3", "bin_4", "bin_5", "bin_6", "bin_7", "bin_8", "bin_9", "bin_10", "bin_11", "bin_12", "bin_13","bin_14", "bin_15", "bin_16", "bin_17", "bin_18", "bin_19", "bin_20")) %>%
  mutate(bin_no = 0:20) %>%
  select(file_name, bin, bin_no, contains("trial"))

# Make data long (using names to both trial and muscle with sep = _)

test_long <- test_bin %>%
  pivot_longer(cols = 4:19, 
               names_to = c("trial", "muscle"), 
               names_sep = "_",
               values_to = "rms") %>%
  arrange(muscle, trial, bin_no) 
```

Ok, so that worked!! Now to run it on all face and non-face files. 
First, need to make a function from the chunk above (function code can be found in extended_cleaning_analysis folder). Done - SF (16/09/20)
Now, set up file path and list, and read in functions. 

## call functions
```{r}
source(here("extended_cleaning_analysis", "cleanwrite_function_extendedanalysis.R"))
```


## set up path and files list
```{r}

# faces
face_filepath <- here("extended_cleaning_analysis", "data", "raw_data", "face")

face_file_list <- list.files(path = face_filepath, pattern='*.xlsx')

# non-faces 
non_filepath <- here("extended_cleaning_analysis", "data", "raw_data", "non-face")

non_file_list <- list.files(path = non_filepath, pattern='*.xlsx')

```

## FACE data first 
```{r message=FALSE, warning=FALSE}
face_list_raw <- face_file_list %>% 
  map(~ read_excel(path = here("extended_cleaning_analysis", "data", "raw_data", "face", .x), range = "A3:AL24")  %>%
        mutate("file_name" = .x))

# get first item of list for testing -ahhh it worked!
face_1 <- face_list_raw[[1]] %>%
  cleanwrite_emg_extended()

```

### write to csv and save to clean_data folder
```{r}
face_cleanwrite <- face_list_raw %>%
  map(~ cleanwrite_emg_extended(.x))
```

### make a df with face files! 
```{r}
df_face <- face_list_raw %>%
  map_df(~ clean_emg_extended(.x))

df_face$rms <- as.numeric(df_face$rms)
df_face$bin <- as.factor(df_face$bin)
df_face$trial <- as.factor(df_face$trial)
df_face$muscle <- as.factor(df_face$muscle)

# write as a csv
write_csv(df_face, here("extended_cleaning_analysis", "data", "clean_data", "faces_clean_extended.csv"))
```


OK faces data is done!! Now, onto non-face data. 

## NON-FACE
```{r message=FALSE, warning=FALSE}
non_list_raw <- non_file_list %>% 
  map(~ read_excel(path = here("extended_cleaning_analysis", "data", "raw_data", "non-face", .x), range = "A3:AL24")  %>%
        mutate("file_name" = .x))

```


### write to csv and save to clean_data folder
```{r}
non_cleanwrite <- non_list_raw %>%
  map(~ cleanwrite_emg_extended(.x))
```

NOTE: pp481_913 - does not work with code so going to do it separately and combine with final df :)
```{r}
pp481_913 <- read_excel(here("extended_cleaning_analysis", "data", "raw_data", "pp481_913.xlsx"), range = "A3:AL24") %>%
  mutate_if(is.character,as.double) %>%
  mutate(file_name = "pp481_913.xlsx") %>%
  remove_empty(which = "cols") %>%
  rename(bin = ...1, 
         trial3_brow = ...12, 
         trial3_cheek = ...13, 
         trial7_brow = ...32, 
         trial7_cheek = ...33) %>%
  mutate(bin = c("bin_0", "bin_1", "bin_2", "bin_3", "bin_4", "bin_5", "bin_6", "bin_7", "bin_8", "bin_9", "bin_10", "bin_11", "bin_12", "bin_13","bin_14", "bin_15", "bin_16", "bin_17", "bin_18", "bin_19", "bin_20")) %>%
  mutate(bin_no = 0:20) %>%
  select(file_name, bin, bin_no, contains("trial")) %>%
  pivot_longer(cols = 4:7, 
               names_to = c("trial", "muscle"), 
               names_sep = "_",
               values_to = "rms") %>%
  arrange(muscle, trial, bin_no)

write_csv(pp481_913, here("extended_cleaning_analysis", "data", "clean_data", "clean_pp481_913.xlsx.csv"))
  
```


### make a df with non-face files! 
```{r}
df_non <- non_list_raw %>%
  map_df(~ clean_emg_extended(.x))

df_non <- rbind(df_non, pp481_913) %>%
  arrange(muscle, trial, bin) 

df_non$rms <- as.numeric(df_non$rms)
df_non$bin <- as.factor(df_non$bin)
df_non$trial <- as.factor(df_non$trial)
df_non$muscle <- as.factor(df_non$muscle)

# write as a csv
write_csv(df_non, here("extended_cleaning_analysis", "data", "clean_data", "non_clean_extended.csv"))

```

