---
title: "2_baseline_outliers"
author: "Sahar Fatima"
date: "16/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(naniar)
library(ggbeeswarm)
library(ggeasy)
library(skimr)

```

# Read in clean data
```{r message=FALSE, warning=FALSE}

face <- read_csv(here("extended_cleaning_analysis", "data", "clean_data", "faces_clean_extended.csv"))

non <- read_csv(here("extended_cleaning_analysis", "data", "clean_data", "non_clean_extended.csv"))

```

## create participant and condition columns out of filename

Use separate() to split the filename into pp_no and condition and mutate with str_sub to drop the last 6 characters off the end of the values in the condition column to get rid of the .xlsx

```{r}
face <- face %>%
  separate(file_name, into = c("pp_no", "condition"), sep = "_") %>% 
  mutate(condition = str_sub(condition, end = -6)) 

non <- non %>%
  separate(file_name, into = c("pp_no", "condition"), sep = "_") %>% 
  mutate(condition = str_sub(condition, end = -6)) 
```


## Combine final FACE and NON-FACE to make data frame with all raw data. 
```{r}
raw_face_nonface <- bind_rows(face, non) %>%
  arrange(pp_no, muscle, condition, trial, bin_no) %>%
  select(pp_no, muscle, condition, trial, bin, bin_no, rms)

write_csv(raw_face_nonface, here("extended_cleaning_analysis", "data", "clean_data", "raw_face_nonface.csv"))
```


# FACE FIRST
## filter out baseline + outliers
if sdRMS > 2 = TRUE, if not = FALSE -> outlier2SD
if sdRMS > 1.5 = TRUE, if not = FALSE -> outlier1.5SD
```{r}
face_BL <- face %>%
  filter(bin == "bin_0") 

face_stat <- face_BL %>%
  group_by(pp_no, muscle, condition) %>%
  mutate(meanRMS = mean(rms), 
         sdRMS = sd(rms))

face_BL_outlier <- face_stat %>%
  mutate("outlier2SD" = if_else(rms > (meanRMS + 2*sdRMS), "TRUE", "FALSE")) %>%
  mutate("outlier1.5SD" = if_else(rms > (meanRMS + 1.5*sdRMS), "TRUE", "FALSE"))

#check if outlier is logical
glimpse(face_BL_outlier)

#make outlier logical
face_BL_outlier$outlier2SD <- as.logical(face_BL_outlier$outlier2SD)
face_BL_outlier$outlier1.5SD <- as.logical(face_BL_outlier$outlier1.5SD)

```

# Now NON-FACE
```{r}
non_BL <- non %>%
  filter(bin == "bin_0") 

non_stat <- non_BL %>%
  group_by(pp_no, muscle, condition) %>%
  mutate(meanRMS = mean(rms), 
         sdRMS = sd(rms))

non_BL_outlier <- non_stat %>%
  mutate("outlier2SD" = if_else(rms > (meanRMS + 2*sdRMS), "TRUE", "FALSE")) %>%
  mutate("outlier1.5SD" = if_else(rms > (meanRMS + 1.5*sdRMS), "TRUE", "FALSE"))

#check if outlier is logical
glimpse(non_BL_outlier)

#make outlier logical
non_BL_outlier$outlier2SD <- as.logical(non_BL_outlier$outlier2SD)
non_BL_outlier$outlier1.5SD <- as.logical(non_BL_outlier$outlier1.5SD)
```
# write to csv

```{r}
write_csv(face_BL_outlier, here("extended_cleaning_analysis", "data", "face_BL_outlier_2000.csv"))

write_csv(non_BL_outlier, here("extended_cleaning_analysis", "data", "non_BL_outlier_2000.csv"))
```

