---
title: "6_lmm_face_analysis_2000"
author: "Sahar Fatima"
date: "16/09/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective 
Analyse cheek and brow muscle activity in response to facial expressions of emotion (i.e., happy and angry faces) from 500 - 2000ms post-stimulus onset. 

## load packages 

```{r message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggeffects)
library(broom.mixed)
library(pixiedust)
library(beepr)
library(effsize)
library(lsmeans)
```


## read in data 
filter out diff_bin1 - diff_bin4
```{r message=FALSE, warning=FALSE}
face <- read_csv(here("extended_cleaning_analysis", "data", "5_face_screened_2000.csv")) %>%
  mutate(condition = recode(condition, "429" = "angry","673" = "happy", .default = "NA")) %>%
  filter(bin != c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4"))

options(scipen = 999)
```

## fix data types 

```{r}
face$condition <- as.factor(face$condition)

face <- face %>% 
  mutate_if(is.character,as.factor) 

face$bin <- fct_relevel(face$bin, c("diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10", "diff_bin11", "diff_bin12", "diff_bin13", "diff_bin14", "diff_bin15", "diff_bin16", "diff_bin17", "diff_bin18", "diff_bin19", "diff_bin20"))

```

## make cheek and brow data frames
```{r}
#face_cheek 
face_cheek <- face %>%
  filter(muscle == "cheek") %>%
  arrange(pp_no, condition, trial, bin)

#face_brow
face_brow <- face %>%
  filter(muscle == "brow") %>%
  arrange(pp_no, condition, trial, bin)
```

# CHEEK

### Cheek MODEL 1 (including all main effects and interactions as fixed effects and random slopes)
This model predicts Zdiff from fixed effects of condition (happy, angry) and bin (1-20), and their interactions (condition x bin).

It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition, bin and their interaction (condition*bin). 

```{r}
# did not converge 

# lm2000_face_cheek_1 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin + condition*bin|pp_no), data = face_cheek, REML = FALSE) 
```

#### Model 1 take home 
Cheek Model 1 did not converge - so going to simplify by removing random slope for the interaction. 

### Cheek MODEL 2 (random slopes for condition and bin)
It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition and bin. 


```{r}
# did not converge

# lm2000_face_cheek_2 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin|pp_no), data = face_cheek, REML = FALSE)
```

### Cheek MODEL 3 (random slopes for condition)
It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition.

```{r}
# converges! 
lm2000_face_cheek_3 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition|pp_no), data = face_cheek, REML = FALSE)
```

#### check if normality assumptions are met 
``` {r}
plot(lm2000_face_cheek_3)

qqnorm(resid(lm2000_face_cheek_3))
qqline(resid(lm2000_face_cheek_3)) 

```

#### transform to correct normality
Usually we would log transform but the Zdiff includes negative values. Alternative is to use a log modulus transform. This transformation log transforms the absolute value (without the -ve) and then puts the sign back on). 
``` {r}
face_cheek <- face_cheek %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))

# run model again

lm2000_face_cheek_3 <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition|pp_no), data = face_cheek, REML = FALSE)
```

#### test assumptions again 
Residuals are more evenly distributed than before; qq plot is better as well.

```{r}
plot(lm2000_face_cheek_3)

qqnorm(resid(lm2000_face_cheek_3))
qqline(resid(lm2000_face_cheek_3)) 

```

#### get anova()/ summary
```{r}
# use anova to estimate effects
aov2000_face_cheek_3 <- anova(lm2000_face_cheek_3) %>%
  rownames_to_column() %>%
  rename(term = rowname)

anova(lm2000_face_cheek_3)

# use summary to get coefficients
summary(lm2000_face_cheek_3)

confint.merMod(lm2000_face_cheek_3, level = 0.95)

```


#### model 3 take home 
so Model 3 converges - main effect for bin is significant. 

In summary table, interactions b/ween condition and some bins is also significant. 

# BROW

### Brow MODEL 1 (including all main effects and interactions as fixed effects and random slopes)
This model predicts Zdiff from fixed effects of condition (happy, angry) and bin (1-10), and their interactions (condition x bin).

It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition, bin and their interaction (condition*bin). 

```{r}
# did not converge 

# lm_face_brow_1 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin + condition*bin|pp_no), data = face_brow, REML = FALSE) 
```

#### Model 1 take home 
Brow Model 1 did not converge - so going to simplify by removing random slope for the interaction. 

### Brow MODEL 2 (random slopes for condition and bin)
It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition and bin. 


```{r}
# fails to converge!

# lm_face_brow_2 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin|pp_no), data = face_brow, REML = FALSE)
```

#### model 2 take home 
Model 2 failed to converge. 

### Brow MODEL 3 (slopes for condition)

```{r}
lm2000_face_brow_3 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition|pp_no), data = face_brow, REML = FALSE)
```


##### check if normality assumptions are met 
``` {r}
plot(lm2000_face_brow_3)

qqnorm(resid(lm2000_face_brow_3))
qqline(resid(lm2000_face_brow_3)) 

```

#### transform to correct normality
Usually we would log transform but the Zdiff includes negative values. Alternative is to use a log modulus transform. This transformation log transforms the absolute value (without the -ve) and then puts the sign back on). 
``` {r}
face_brow <- face_brow %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))

# run model again 

lm2000_face_brow_3 <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition|pp_no), data = face_brow, REML = FALSE)
```


#### test assumptions again 
Residuals are more evenly distributed than before; qq plot is better as well.

```{r}
plot(lm2000_face_brow_3)

qqnorm(resid(lm2000_face_brow_3))
qqline(resid(lm2000_face_brow_3))

```


### get anova()/ summary
```{r}
aov2000_face_brow_3 <- anova(lm2000_face_brow_3) %>%
  rownames_to_column() %>%
  rename(term = rowname)

anova(lm2000_face_brow_3)
summary(lm2000_face_brow_3)

confint.merMod(lm2000_face_brow_3, level = 0.95)

```

#### model 3 take home
no main effects nor interactions are significant. 
