---
title: "7_lmm_nonface_analysis_2000"
author: "Sahar Fatima"
date: "16/09/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective:
Analyse chee and brow responding to positively- and negatively-valenced non-facial stimuli for an extended time period (i.e., 500 - 2000ms post-stimulus onset). 

## load packages 

```{r message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggeffects)
library(broom.mixed)
library(pixiedust)
library(beepr)
library(effsize)
library(lsmeans)
```


## read in data 
filter out diff_bin1 - diff_bin4
```{r message=FALSE, warning=FALSE}
non <- read_csv(here("extended_cleaning_analysis", "data", "5_non_screened_2000.csv")) %>%
  mutate(condition = recode(condition, "913" = "negative","285" = "positive", .default = "NA")) %>%
  filter(bin != c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4"))

options(scipen = 999)
```

## fix data types 

```{r}
non$condition <- as.factor(non$condition)

non <- non %>% 
  mutate_if(is.character,as.factor)

non$bin <- fct_relevel(non$bin, c("diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10", "diff_bin11", "diff_bin12", "diff_bin13", "diff_bin14", "diff_bin15", "diff_bin16", "diff_bin17", "diff_bin18", "diff_bin19", "diff_bin20"))

```


## make cheek and brow data frames
```{r}
#non_cheek 
non_cheek <- non %>%
  filter(muscle == "cheek") %>%
  arrange(pp_no, condition, trial, bin)

#non_brow
non_brow <- non %>%
  filter(muscle == "brow") %>%
  arrange(pp_no, condition, trial, bin)
```

# CHEEK 

### Cheek MODEL 1 (including all main effects and interactions as fixed effects and random slopes)
This model predicts Zdiff from fixed effects of condition (happy, angry) and bin (1-10), and their interactions (condition x bin).

It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition, bin and their interaction (condition*bin). 

```{r}
# did not converge 

# lm2000_non_cheek_1 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin + condition*bin|pp_no), data = non_cheek, REML = FALSE) 
```

#### Model 1 take home 
Cheek Model 1 did not converge - so going to simplify by removing random slope for the interaction. 

### Cheek MODEL 2 (random slopes for condition and bin)
It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition and bin. 


```{r}
# does not converge

# lm2000_non_cheek_2 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin|pp_no), data = non_cheek, REML = FALSE)
```


### Cheek MODEL 3 (random slopes for condition)
It includes random intercepts for participant (accounting for the potential of some kids to just have more active nons than others) and random slopes for condition.

```{r}
# converges! 
lm2000_non_cheek_3 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition|pp_no), data = non_cheek, REML = FALSE)
```

##### check if normality assumptions are met 
``` {r}
plot(lm2000_non_cheek_3)

qqnorm(resid(lm2000_non_cheek_3))
qqline(resid(lm2000_non_cheek_3)) 

```

#### transform to correct normality
Usually we would log transform but the Zdiff includes negative values. Alternative is to use a log modulus transform. This transformation log transforms the absolute value (without the -ve) and then puts the sign back on). 
``` {r}
non_cheek <- non_cheek %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))

# run model again

lm2000_non_cheek_3 <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition|pp_no), data = non_cheek, REML = FALSE)
```

#### test assumptions again 

```{r}
plot(lm2000_non_cheek_3)

qqnorm(resid(lm2000_non_cheek_3))
qqline(resid(lm2000_non_cheek_3))

```


#### get anova()/ summary
```{r}
# use anova to estimate effects
aov2000_non_cheek_3 <- anova(lm2000_non_cheek_3) %>%
  rownames_to_column() %>%
  rename(term = rowname)

anova(lm2000_non_cheek_3)
# use summary to get coefficients
summary(lm2000_non_cheek_3)

confint.merMod(lm2000_non_cheek_3, level = 0.95)
```


#### model 3 take home 
main effects for both condition and bin are significant. Interaction is not. 

# BROW
### Brow MODEL 1 (including all main effects and interactions as fixed effects and random slopes)
This model predicts Zdiff from fixed effects of condition (happy, angry) and bin (1-10), and their interactions (condition x bin).

It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition, bin and their interaction (condition*bin). 

```{r}
# did not converge 

# lm2000_non_brow_1 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin + condition*bin|pp_no), data = non_brow, REML = FALSE) 
```

#### Model 1 take home 
Brow Model 1 did not converge - so going to simplify by removing random slope for the interaction. 

### Brow MODEL 2 (random slopes for condition and bin)
It includes random intercepts for participant (accounting for the potential of some kids to just have more active faces than others) and random slopes for condition and bin. 


```{r}
# failed to converge

# lm2000_non_brow_2 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition + bin|pp_no), data = non_brow, REML = FALSE)
```

#### model 2 take home 
Failed to converge 
Going to compare with simpler model (with slopes for condition only)

### Brow MODEL 3 (slopes for condition)

```{r}
lm2000_non_brow_3 <- lmer(Zdiff ~ condition + bin + condition*bin + (1 + condition|pp_no), data = non_brow, REML = FALSE)
```


##### check if normality assumptions are met 
``` {r}
plot(lm2000_non_brow_3)

qqnorm(resid(lm2000_non_brow_3))
qqline(resid(lm2000_non_brow_3)) 

```

#### transform to correct normality
Usually we would log transform but the Zdiff includes negative values. Alternative is to use a log modulus transform. This transformation log transforms the absolute value (without the -ve) and then puts the sign back on). 
``` {r}
non_brow <- non_brow %>%
  mutate(log_modulus = sign(Zdiff) * log(1+abs(Zdiff)))

# run model again

## did not converge 
lm2000_non_brow_3 <- lmer(log_modulus ~ condition + bin + condition*bin + (1 + condition|pp_no), data = non_brow, REML = FALSE)
```


#### test assumptions again 
Residuals are more evenly distributed than before; qq plot is better as well.

```{r}
plot(lm2000_non_brow_3)

qqnorm(resid(lm2000_non_brow_3))
qqline(resid(lm2000_non_brow_3)) 
```


### get anova()/ summary
```{r}
aov2000_non_brow_3 <- anova(lm2000_non_brow_3) %>%
  rownames_to_column() %>%
  rename(term = rowname)

anova(lm2000_non_brow_3)
summary(lm2000_non_brow_3)
```

#### model 3 take home
Brow model 3 converges - neither main effects nor interaction are significant. 
