---
title: "8_plotting"
author: "Sahar Fatima"
date: "17/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load packages 
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(papaja)
```

## read in screened bin data for faces and non_face

```{r message=FALSE, warning=FALSE}
face <- read_csv(here("extended_cleaning_analysis", "data", "5_face_screened_2000.csv")) %>%
  mutate(condition = recode(condition, "429" = "Angry","673" = "Happy", .default = "NA")) %>%
  filter(bin != c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4"))

non <- read_csv(here("extended_cleaning_analysis", "data", "5_non_screened_2000.csv")) %>%
  mutate(condition = recode(condition, "913" = "Negative","285" = "Positive", .default = "NA")) %>%
  filter(bin != c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4"))
```

## fix bin values 

```{r}
face$bin <- str_sub(face$bin, -4) 

non$bin <- str_sub(non$bin, -4)
```
 
## fix variable types 
```{r}
face$condition <- as.factor(face$condition)
face$trial <- as.factor(face$trial)
face$bin <- as.factor(face$bin)

non$condition <- as.factor(non$condition)
non$trial <- as.factor(non$trial)
non$bin <- as.factor(non$bin)


```


## PLOT FACE - Extended

### CHEEK and BROW - averaged across time - Figure 11
```{r}
face$muscle <- factor(face$muscle, levels = c("cheek", "brow"))

bar_face_2000 <- face %>%
  group_by(condition, muscle) %>%
   summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = muscle, y = meanZ, group = condition, fill = condition)) + 
  geom_bar(stat = "identity", 
           width = 0.9, 
           position = "dodge") + 
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr),
                  size=.4,    # Thinner lines
                    width=.2,
                      position=position_dodge(.9)) + 
  geom_hline(yintercept = 0) +
  theme_apa(box = TRUE) + 
  theme(legend.title = element_text(hjust = 0.5)) +
  theme(legend.position = c(0.12, 0.20), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'), 
        legend.title = element_blank()) + 
  scale_x_discrete(labels = c("brow" = "Brow", "cheek" = "Cheek")) +
  scale_y_continuous(limits = c(-0.15, 0.10), expand = c(0,0)) + 
  scale_fill_grey(end = 0.7, start = 0.4) +
  xlab("Face Muscle") + 
  ylab("Mean z-score difference (RMS) from baseline \n (averaged across bin)") 
  
bar_face_2000


ggsave("face_stimulus_2000_plot.png", path = here("extended_cleaning_analysis", "plots")) 
```

### CHEEK - avg.d across stimulus type - Figure 12

```{r}
face_cheek_bin2000 <- face %>%
  filter(muscle == "cheek") %>%
  group_by(bin) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ)) + 
  geom_point() +
  geom_line(aes(group = 1)) +
  geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr),
                  size=.4,    # Thinner lines
                    width=.2,
                      position=position_dodge(.9)) + 
  geom_hline(yintercept = 0) +
  theme_apa(box = TRUE) + 
  theme(axis.text.x = element_text(size = 8)) + 
  scale_fill_grey() + 
  scale_y_continuous(limits = c(-0.20, 0.25)) + 
  scale_x_discrete(labels = c("bin5" = "Bin 5", "bin6" = "Bin 6", "bin7" = "Bin 7", "bin8" = "Bin 8", "bin9" = "Bin 9", "in10" = "Bin 10", "in11" = "Bin 11", "in12" = "Bin 12", "in13" = "Bin 13", "in14" = "Bin 14", "in15" = "Bin 15", "in16" = "Bin 16", "in17" = "Bin 17", "in18" = "Bin 18", "in19" = "Bin 19", "in20" = "Bin 20")) +
  xlab("Bin") + 
  ylab("Mean z-score differences in cheek responding \n (averaged across facial stimuli)")

print(face_cheek_bin2000)

ggsave("cheek_bin_2000.png", path = here("extended_cleaning_analysis", "plots")) 

```


### CHEEK - Changes in Facial muscle activity over time - Figure 13
```{r}

face_cheek_plot_2000 <- face %>%
  filter(muscle == "cheek") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    # Thinner lines
                    width=.2) + 
  theme_apa(box = TRUE) +
  theme(legend.position = c(0.15, 0.8), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'),
        legend.key.height = unit(0.5, "cm"), 
        legend.title = element_blank()) + 
  ylab("Mean differences in cheek activity \n (baseline-corrected z-score)") + 
  xlab("Time after stimulus presentation (ms)") +
  scale_x_discrete(labels = c("bin5" = "500", "bin6" = "600", "bin7" = "700", "bin8" = "800", "bin9" = "900", "in10" = "1000", "in11" = "1100", "in12" = "1200", "in13" = "1300", "in14" = "1400", "in15" = "1500", "in16" = "1600", "in17" = "1700", "in18" = "1800", "in19" = "1900", "in20" = "2000")) +
  scale_y_continuous(limits = c(-0.2, 0.3)) + 
  scale_color_grey(end = 0.7)

print(face_cheek_plot_2000)

ggsave("cheek_face_2000.png", path = here("extended_cleaning_analysis", "plots")) 
```

### BROW - Changes in Facial muscle activity over time - Figure 14

```{r}
face_brow_plot_2000 <- face %>%
  filter(muscle == "brow") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    # Thinner lines
                    width=.2) + 
  theme_apa(box = TRUE) +
  theme(legend.position = c(0.15, 0.8), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'),
        legend.key.height = unit(0.5, "cm"), 
        legend.title = element_blank()) + 
  ylab("Mean differences in brow activity \n (baseline-corrected z-score)") + 
  xlab("Time after stimulus presentation (ms)") +
  scale_x_discrete(labels = c("bin5" = "500", "bin6" = "600", "bin7" = "700", "bin8" = "800", "bin9" = "900", "in10" = "1000", "in11" = "1100", "in12" = "1200", "in13" = "1300", "in14" = "1400", "in15" = "1500", "in16" = "1600", "in17" = "1700", "in18" = "1800", "in19" = "1900", "in20" = "2000")) +
  scale_y_continuous(limits = c(-0.3, 0.25)) + 
  scale_color_grey(end = 0.7)

print(face_brow_plot_2000)

ggsave("brow_face_2000.png", path = here("extended_cleaning_analysis", "plots")) 

```


## PLOT NON-FACE - Extended

### CHEEK and BROW - averaged across time - Figure 15
```{r}
non$muscle <- factor(non$muscle, levels = c("cheek", "brow"))

bar_non_2000 <- non %>%
  group_by(condition, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = muscle, y = meanZ, group = condition, fill = condition)) + 
  geom_bar(stat = "identity", 
           width = 0.9, 
           position = "dodge") + 
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr),
                  size=.4,    # Thinner lines
                    width=.2,
                      position=position_dodge(.9)) + 
  geom_hline(yintercept = 0) +
  theme_apa(box = TRUE) + 
  theme(legend.position = c(0.85, 0.80), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'), 
        legend.title = element_blank()) + 
  scale_x_discrete(labels = c("brow" = "Brow", "cheek" = "Cheek")) +
  scale_y_continuous(limits = c(-0.15, 0.2), expand = c(0,0)) + 
  scale_fill_grey(end = 0.7, start = 0.4) +
  xlab("Face Muscle") + 
  ylab("Mean z-score difference (RMS) from baseline \n (averaged across bin)") 
  

bar_non_2000

ggsave("bar_nonface_2000.png", path = here("extended_cleaning_analysis", "plots")) 
```


### CHEEK - activity averaged across stimulus type - Figure 16
```{r}
non2000_cheek_bin <- non %>%
  filter(muscle == "cheek") %>%
  group_by(bin) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = bin)) + 
  geom_line(aes(group = 1)) +
  geom_point() +
  geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr),
                  size=.4,    
                    width=.2,
                      position=position_dodge(.9)) + 
  geom_hline(yintercept = 0) +
  theme_apa(box = TRUE) + 
  theme(axis.text.x = element_text(size = 8)) + 
  scale_fill_grey() + 
  scale_x_discrete(labels = c("bin5" = "Bin 5", "bin6" = "Bin 6", "bin7" = "Bin 7", "bin8" = "Bin 8", "bin9" = "Bin 9", "in10" = "Bin 10", "in11" = "Bin 11", "in12" = "Bin 12", "in13" = "Bin 13", "in14" = "Bin 14", "in15" = "Bin 15", "in16" = "Bin 16", "in17" = "Bin 17", "in18" = "Bin 18", "in19" = "Bin 19", "in20" = "Bin 20")) + 
  scale_y_continuous(limits = c(-0.20, 0.3), 
                     expand  = c(0, 0)) + 
  xlab("Bin") +
  ylab("Mean z-score differences in cheek responding \n (averaged across non-facial stimuli)")

print(non2000_cheek_bin)

ggsave("cheek_non_bin_2000.png", path = here("extended_cleaning_analysis", "plots")) 
```

### CHEEK - Changes in Facial muscle activity over time - Figure 17

```{r}
non$condition <- factor(non$condition, levels = c("Positive", "Negative"))

non_cheek_plot_2000 <- non %>%
  filter(muscle == "cheek") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    
                    width=.2) + 
  theme_apa(box = TRUE) +
  theme(legend.position = c(0.15, 0.8), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'),
        legend.key.height = unit(0.5, "cm"), 
        legend.title = element_blank()) + 
  ylab("Mean differences in cheek activity \n (baseline-corrected z-score)") + 
  xlab("Time after stimulus presentation (ms)") +
  scale_x_discrete(labels = c("bin5" = "500", "bin6" = "600", "bin7" = "700", "bin8" = "800", "bin9" = "900", "in10" = "1000", "in11" = "1100", "in12" = "1200", "in13" = "1300", "in14" = "1400", "in15" = "1500", "in16" = "1600", "in17" = "1700", "in18" = "1800", "in19" = "1900", "in20" = "2000")) +
  scale_y_continuous(limits = c(-0.2, 0.4)) + 
  scale_color_grey(start = 0.3, end = 0.7)

print(non_cheek_plot_2000)

ggsave("cheek_nonface_2000.png", path = here("extended_cleaning_analysis", "plots"))
```

## BROW - activity across time - Figure 18
```{r}

non_brow_plot_2000 <- non %>%
  filter(muscle == "brow") %>%
  group_by(condition, bin, muscle) %>%
  summarise(meanZ = mean(Zdiff, na.rm = TRUE), 
            sd_RMS = sd(Zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = bin, y = meanZ, group = condition, colour = condition)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = meanZ - stderr, ymax = meanZ + stderr), 
                size=.5,    
                    width=.2) + 
  theme_apa(box = TRUE) +
  theme(legend.position = c(0.15, 0.20), 
        legend.background = element_rect(colour = 'black', 
                                           linetype='solid'),
        legend.key.height = unit(0.5, "cm"), 
        legend.title = element_blank()) + 
  ylab("Mean differences in brow activity \n (baseline-corrected z-score)") + 
  xlab("Time after stimulus presentation (ms)") +
  scale_x_discrete(labels = c("bin5" = "500", "bin6" = "600", "bin7" = "700", "bin8" = "800", "bin9" = "900", "in10" = "1000", "in11" = "1100", "in12" = "1200", "in13" = "1300", "in14" = "1400", "in15" = "1500", "in16" = "1600", "in17" = "1700", "in18" = "1800", "in19" = "1900", "in20" = "2000")) +
  scale_y_continuous(limits = c(-0.3, 0.2)) + 
  scale_color_grey(end = 0.7)

print(non_brow_plot_2000)

ggsave("brow_non_bin_2000.png", path = here("extended_cleaning_analysis", "plots"))
```
