---
title: "12_plotting_brow"
output: html_document
---

# load packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(broom.mixed)
library(ggplot2) 
library(ggeasy)
library(dplyr)
library(RColorBrewer)
library(papaja)
library(lubridate)
library(harrypotter)
```

# read in data 
```{r}
df <- read_csv(here::here("data", "adult_child_combined", "zdiff_binscreened2.csv"))
```

# fix data types

```{r}
df$emotion <- as.factor(df$emotion)

levels(df$emotion)

df <- df %>% mutate_if(is.character, as.factor)

glimpse(df)
```


#CHILD BROW

```{r}
plot_child_brow <- df %>%
  filter(emo %in% c("Happy", "Angry", "Fear", "Sad")) %>%
  filter(emotion %in% c("121", "323", "424", "525")) %>%
  filter(muscle == "brow") %>%
  filter(model == "child") %>%
  arrange(pp_no, emotion, emo, trial, bin)

glimpse(plot_child_brow)
```

#make sure it is only the relevant emotions
```{r}

plot_child_brow$emo <- fct_relevel(plot_child_brow$emo, c("Happy", "Angry", "Fear", "Sad"))

plot_child_brow$emotion <- fct_relevel(plot_child_brow$emotion, c("121", "323", "424", "525"))

levels(plot_child_brow$emo)


plot_child_brow$bin <- fct_relevel(plot_child_brow$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

levels(plot_child_brow$bin)
```

#create a new bin column and rename bins
```{r}

plot_child_brow$time_bin <- plot_child_brow$bin


plot_child_brow <- plot_child_brow %>%
  mutate(time_bin = recode(bin, "diff_bin1" = "100",
                                "diff_bin2" = "200", 
                                "diff_bin3" = "300", 
                                "diff_bin4" = "400", 
                              "diff_bin5" = "500", 
                              "diff_bin6" = "600", 
                              "diff_bin7" = "700", 
                              "diff_bin8" = "800",
                              "diff_bin9" = "900",
                              "diff_bin10" = "1000", .default = "NA"))
                           
                      
```



#plot brow activity 

emotion x bin - all emotions 

```{r}
plot_all_child <- plot_child_brow %>%
  filter(model == "child") %>%
  filter(emo %in% c("Happy", "Angry", "Fear", "Sad")) %>%
  filter(emotion %in% c("121", "323", "424", "525")) %>%
  filter(muscle == "brow") %>%
  group_by(emo, time_bin, emotion) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
  scale_colour_grey(start = 0.0, end = 0.8) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  theme_apa() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(y = "Mean difference in brow activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
easy_x_axis_title_size(size = 16) +
 easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 20) +
  easy_plot_legend_size(size = 20) +
  easy_add_legend_title("Emotion") +
  labs(subtitle = "D") +
  easy_plot_title_size(size = 20) +
  easy_plot_subtitle_size(size = 18)
  

print(plot_all_child)

ggsave("brow_child_D.png")
```

#happy/angry 

emotion x bin  

```{r}
plot_child_HA <- plot_child_brow %>%
  filter(model == "child") %>%
  filter(emo %in% c("Happy", "Angry")) %>%
  filter(emotion %in% c("121", "323")) %>%
  filter(muscle == "brow") %>%
  group_by(emo, time_bin, emotion) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme_apa() +
  scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(y = "Mean difference in brow activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
easy_x_axis_title_size(size = 16) +
 easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 20) +
  easy_plot_legend_size(size = 20) +
  easy_add_legend_title("Emotion") +
  labs(subtitle = "A") +
  labs(title = "Child Brow") +
  easy_plot_title_size(size = 20) +
  easy_plot_subtitle_size(size = 18)
  

print(plot_child_HA)

ggsave("brow_child_A.png")
```

#happy/fear

emotion x bin 
```{r}
plot_child_HF <- plot_child_brow %>%
  filter(model == "child") %>%
  filter(emo %in% c("Happy", "Fear")) %>%
  filter(emotion %in% c("121", "424")) %>%
  filter(muscle == "brow") %>%
  group_by(emo, time_bin, emotion) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
  scale_colour_grey(start = 0.3, end = 0.6) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme_apa() +
  scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(y = "Mean difference in brow activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
 easy_x_axis_title_size(size = 16) +
 easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 20) +
  easy_plot_legend_size(size = 20) +
  easy_add_legend_title("Emotion") +
  labs(subtitle = "B") +
  easy_plot_title_size(size = 20) +
  easy_plot_subtitle_size(size = 18)
  

print(plot_child_HF)

ggsave("brow_child_B.png")
```
#hapyy/sad

emotion x bin
```{r}
plot_child_HS <- plot_child_brow %>%
  filter(model == "child") %>%
  filter(emo %in% c("Happy", "Sad")) %>%
  filter(emotion %in% c("121", "525")) %>%
  filter(muscle == "brow") %>%
  group_by(emo, time_bin, emotion) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
    scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme_apa() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(y = "Mean difference in brow activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
 easy_x_axis_title_size(size = 16) +
 easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 20) +
  easy_plot_legend_size(size = 20) +
  easy_add_legend_title("Emotion") +
  labs(subtitle = "C") +
  easy_plot_title_size(size = 20) +
  easy_plot_subtitle_size(size = 18)
  

print(plot_child_HS)

ggsave("brow_child_C.png")
```


#adult BROW

```{r}
plot_adult_brow <- df %>%
  filter(emo %in% c("Happy", "Angry", "Fear", "Sad")) %>%
  filter(emotion %in% c("131", "232", "434", "535")) %>%
  filter(model == "adult") %>%
  arrange(pp_no, emotion, emo, muscle, trial, bin)

glimpse(plot_adult_brow)
```

#make sure it is only the relevant emotions
```{r}

plot_adult_brow$emo <- fct_relevel(plot_adult_brow$emo, c("Happy", "Angry", "Fear", "Sad"))

levels(plot_adult_brow$emo)

plot_adult_brow$emotion <- fct_relevel(plot_adult_brow$emotion, c("131", "232", "434", "535"))

plot_adult_brow$bin <- fct_relevel(plot_adult_brow$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

levels(plot_adult_brow$bin)
```

#create a new bin column and rename bins
```{r}

plot_adult_brow$time_bin <- plot_adult_brow$bin


plot_adult_brow <- plot_adult_brow %>%
  mutate(time_bin = recode(bin, "diff_bin1" = "100",
                                "diff_bin2" = "200", 
                                "diff_bin3" = "300", 
                                "diff_bin4" = "400", 
                              "diff_bin5" = "500", 
                              "diff_bin6" = "600", 
                              "diff_bin7" = "700", 
                              "diff_bin8" = "800",
                              "diff_bin9" = "900",
                              "diff_bin10" = "1000", .default = "NA"))
                           
                      
```



#plot brow activity 

emotion x bin - all emotions 

```{r}
plot_adult <- plot_adult_brow %>%
  filter(model == "adult") %>%
  filter(emo %in% c("Happy", "Sad", "Angry", "Fear")) %>%
  filter(muscle == "brow") %>%
  group_by(emo, time_bin, emotion) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
    scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme_apa() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(y = "Mean difference in brow activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
 easy_x_axis_title_size(size = 16) +
 easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 20) +
  easy_plot_legend_size(size = 20) +
  easy_add_legend_title("Emotion") +
  labs(subtitle = "D") +
  easy_plot_title_size(size = 20) +
  easy_plot_subtitle_size(size = 18)
  

print(plot_adult)

ggsave("brow_adult_D.png")
```

#happy/fear 

emotion x bin 
```{r}
plot_adult <- plot_adult_brow %>%
  filter(model == "adult") %>%
  filter(emo %in% c("Happy", "Fear")) %>%
  filter(muscle == "brow") %>%
  group_by(emo, time_bin, emotion) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
    scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme_apa() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(y = "Mean difference in brow activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
 easy_x_axis_title_size(size = 16) +
 easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 20) +
  easy_plot_legend_size(size = 20) +
  easy_add_legend_title("Emotion") +
  labs(subtitle = "B") +
  easy_plot_title_size(size = 20) +
  easy_plot_subtitle_size(size = 18)
  

print(plot_adult)

ggsave("brow_adult_B.png")
```

#happy/angry

emotion x bin 
```{r}
plot_adult <- plot_adult_brow %>%
  filter(model == "adult") %>%
  filter(emo %in% c("Happy", "Angry")) %>%
  filter(muscle == "brow") %>%
  group_by(emo, time_bin, emotion) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
    scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme_apa() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(y = "Mean difference in brow activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
 easy_x_axis_title_size(size = 16) +
 easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 20) +
  easy_plot_legend_size(size = 20) +
  easy_add_legend_title("Emotion") +
  labs(subtitle = "A") +
  labs(title = "Adult Brow") +
  easy_plot_title_size(size = 20) +
  easy_plot_subtitle_size(size = 18)
  

print(plot_adult)

ggsave("brow_adult_A.png")
```

#happy/sad

emotion x bin 
```{r}
plot_adult <- plot_adult_brow %>%
  filter(model == "adult") %>%
  filter(emo %in% c("Happy", "Sad")) %>%
  filter(muscle == "brow") %>%
  group_by(emo, time_bin, emotion) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), sd_RMS = sd(zdiff, na.rm = TRUE), n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
    scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme_apa() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(y = "Mean difference in brow activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
 easy_x_axis_title_size(size = 16) +
 easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 20) +
  easy_plot_legend_size(size = 20) +
  easy_add_legend_title("Emotion") +
  labs(subtitle = "C") +
  easy_plot_title_size(size = 20) +
  easy_plot_subtitle_size(size = 18)
  

print(plot_adult)

ggsave("brow_adult_C.png")
```




