---
title: "adult_child_analysis"
output:
  word_document: default
  html_document: default
---


# load packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(pixiedust)
library(beepr)
library(ggplot2) 
library(ggeasy)
library(dplyr)
library(papaja)
library(knitr)
library(harrypotter)
library(hexbin)
library(stringr)
```

the goal here is to work out whether it is possible to compare responses to child and adult faces i.e. to include model in the model. 

# read in data 
```{r}
df <- read_csv(here::here("data", "adult_child_combined", "zdiff_binscreened2.csv"))
```


### fix data types and add log modulus
```{r}

df <- df %>% mutate_if(is.character, as.factor) %>%
  mutate(log_modulus = sign(zdiff) * log(1+abs(zdiff)))
  
glimpse(df)
```

# CHEEK happy-angry-fear-sad

### Make cheek df 
```{r}
cheek_data <- df %>%
  filter(emo %in% c("Happy", "Angry","Fear", "Sad")) %>%
  filter(muscle == "cheek") %>%
  arrange(pp_no, model, trial, bin)

cheek_data$emo <- fct_relevel(cheek_data$emo, c("Happy", "Angry", "Fear", "Sad"))

cheek_data$bin <- fct_relevel(cheek_data$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

levels(cheek_data$bin)

naniar::vis_miss(cheek_data)
```

add "model" to best fit from 9_cheek_analysis 

## model 1 (slopes emo)

This model adds model to best fit model (including slopes for emo)

> adult_cheek_lm_2 <- lmer(log_modulus ~ emo + bin + emo*bin + (1 + emo|pp_no) , data = HA_adult_cheek, REML = FALSE)

```{r}
cheek_lm_1 <- lmer(log_modulus ~ emo + bin + model + 
                    emo*bin + bin*model +
                    emo*bin*model +
                    (1 + emo|pp_no) , 
                  data = cheek_data, REML = FALSE)

beepr::beep()
```


## model 2 (just intercepts participant)
```{r}
cheek_lm_2 <- lmer(log_modulus ~ emo + bin + model + 
                    emo*bin + bin*model +
                    emo*bin*model +
                    (1|pp_no) , 
                  data = cheek_data, REML = FALSE)

beepr::beep()
```


# compare models with and without slopes

Model with slope (cheek_lm_1 AIC = 27557) does better than model without (cheek_lm_1 AIC = 28261). 

```{r}
AIC(cheek_lm_1)
AIC(cheek_lm_2)

anova(cheek_lm_1, cheek_lm_2)
```

### get summary/tidydf

```{r}
summary(cheek_lm_1)

tidy_cheek1 <- tidy(cheek_lm_1)
```


#get anova
```{r}
aov_output <- anova(cheek_lm_1)

nice_aov <- dust(aov_output) %>%
  sprinkle(col = 1:6, round = 3, pad = 15, halign = "center", valign = "middle") %>% 
  sprinkle(col = 6, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
   sprinkle_print_method("html") 

nice_aov
```


```{r}
anova(cheek_lm_1)
```


#get confidence intervals 
```{r cache = TRUE}
confint.merMod(cheek_lm_1, level = 0.95)
```


#get really nice table
```{r}
really_nice_table <- dust(cheek_lm_1) %>%
  sprinkle(col = 4:7, round = 3, pad = 15, halign = "center", valign = "middle") %>%
  sprinkle(col = 8, fn = quote(pvalString(value)), halign = "center", valign = "middle") %>%
  sprinkle_colnames(term = "Term", 
                    estimate = "Estimate", 
                    std.error = "SE",
                    statistic = "t statistic", 
                    p.value = "P-value")  %>%
  sprinkle(bg_pattern_by = "rows") %>%
    sprinkle_print_method("html") 

really_nice_table
```


# CHEEK plots 

### plot cheek data for all emo 

```{r}
cheek_plot <- cheek_data %>%
  filter(muscle == "cheek") %>%
  arrange(pp_no, emotion, model, trial, bin) 


glimpse(cheek_data)

cheek_data$model <- as.factor(cheek_plot$model)

glimpse(cheek_plot)
```


# create new column called time_bin
```{r}

cheek_plot$time_bin <- cheek_plot$bin


cheek_plot <- cheek_plot %>%
  mutate(time_bin = recode(bin, "diff_bin1" = "100",
                                "diff_bin2" = "200", 
                                "diff_bin3" = "300", 
                                "diff_bin4" = "400", 
                              "diff_bin5" = "500", 
                              "diff_bin6" = "600", 
                              "diff_bin7" = "700", 
                              "diff_bin8" = "800",
                              "diff_bin9" = "900",
                              "diff_bin10" = "1000", .default = "NA"))

cheek_plot$emotion <- as.factor(cheek_plot$emotion)


glimpse(cheek_plot)

```



### emotion x model

```{r cplot1}
cplot1 <- cheek_plot %>%
  group_by(time_bin, model, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), 
            sd_RMS = sd(zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme_apa() +
  scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  facet_wrap(~ model) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(title = "cheek", y = "Mean difference in muscle activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
  easy_x_axis_title_size(size = 16) +
  easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 16) +
  easy_plot_legend_size(size = 16) +
  easy_add_legend_title("Emotion") +
  easy_plot_title_size(size = 20) +
  easy_x_axis_labels_size(size = 7)

print(cplot1)

ggsave("emotionbymodel.png")

```

 
### emotion x model (HappyAngry)
```{r cplot2}
cplot2 <- cheek_plot %>%
  filter(emo %in% c("Happy", "Happy", "Angry", "Angry")) %>%
  group_by(time_bin, model, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), 
            sd_RMS = sd(zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = model, colour = emo)) +
  geom_point() +
  geom_line() +
  scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme_apa() +
  facet_wrap(~emo) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.3)) +
  labs(title = "cheek", y = "Mean difference in muscle activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
  easy_x_axis_title_size(size = 16) +
  easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 16) +
  easy_plot_legend_size(size = 16) +
  easy_add_legend_title("Emotion") +
  easy_plot_title_size(size = 20) +
  easy_x_axis_labels_size(size = 7)

cplot2

ggsave("emoxmodelHA.png")

```


### emotion x model (FearSad)
```{r cplot3}
cplot3 <- cheek_plot %>%
  filter(emo %in% c("Fear", "Sad")) %>%
  group_by(time_bin, model, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), 
            sd_RMS = sd(zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
  scale_color_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_classic() +
  theme_apa() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  facet_wrap(~ model) +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(title = "cheek", y = "Mean difference in muscle activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
   easy_x_axis_title_size(size = 16) +
  easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 14) +
  easy_plot_legend_title_size(size = 16) +
  easy_plot_legend_size(size = 16) +
  easy_add_legend_title("Emotion") +
  easy_plot_title_size(size = 20) +
  easy_x_axis_labels_size(size = 7)


cplot3

ggsave("emoxmodelFS.png")

```


# plot averaged across bins - bar graphs 
```{r cplot4_5}
 
cplot4 <- cheek_plot %>%
  group_by(model, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), 
            sd_RMS = sd(zdiff, na.rm = TRUE), 
            n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = emo, y = meanZ, fill = emo)) +
  geom_col(position = "dodge") +
  theme_apa(base_size = 14) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4, position = position_dodge(.9)) +
  scale_fill_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  theme_classic() +
  theme_apa() +
  facet_wrap(~model) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(limits = c(-0.1, 0.1)) +
  labs(title = "Cheek", y = "Mean z-score difference (RMS) from baseline
(averaged across bins)", x = "Emotion") +
  easy_x_axis_title_size(size = 14) +
  easy_y_axis_title_size(size = 14)

cplot4 

cplot5 <- cheek_plot %>%
  group_by(model, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), 
            sd_RMS = sd(zdiff, na.rm = TRUE), 
            n = n(), stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = emo, y = meanZ, fill = emo)) +
  geom_col(position = "dodge") +
  theme_apa(base_size = 14) +
  scale_fill_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4, position = position_dodge(.9)) +
  theme_classic() +
  facet_wrap(~model) +
 theme_apa() +
  scale_y_continuous(limits = c(-0.1, 0.1)) +
  geom_hline(yintercept = 0) +
  labs(title = "Cheek", y = "Mean z-score difference (RMS) from baseline
(averaged across bins)", x = "Emotion") +
  easy_x_axis_title_size(size = 14) +
  easy_y_axis_title_size(size = 14) +
  easy_remove_legend() +
  easy_x_axis_labels_size(size = 12) +
  easy_y_axis_labels_size(size = 12)
  

cplot5
  
ggsave("emomodelnobins.png")

```

Eyeballing CHEEK output. Looks like we have significant bin differences late in the trial (bin8, bin9, bin10) and sig emotion x bin differences late in the trial (bin8 and bin9) for angry - this is shown in the following plot

```{r}
print(cplot2)
```


It is surprising that the model x bin x emo effects late in the trial are not sig, because the emo x bin difference seems to be driven by differences in adult. BUT, the effect of model isn't significant so we should probably average across child and adult in the plot

#happy/angry averaged across model
```{r cplot6}
cplot6 <- cheek_plot %>%
  filter(emo %in% c("Happy", "Angry")) %>%
  group_by(time_bin, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), 
            sd_RMS = sd(zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = time_bin, y = meanZ, group = emo, colour = emo)) +
  geom_point() +
  geom_line() +
  scale_colour_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_apa() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(title = "Cheek", y = "Mean difference in muscle activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
  easy_x_axis_title_size(size = 16) +
  easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 12) +
  easy_plot_legend_title_size(size = 16) +
  easy_plot_legend_size(size = 14) +
  easy_add_legend_title("Emotion") +
  easy_plot_title_size(size = 16) +
  easy_x_axis_labels_size(size = 12)

cplot6

ggsave("avgxmodel.png")
```


```{r cplot6}
cplot7 <- cheek_plot %>%
  filter(emo %in% c("Happy", "Angry", "Fear", "Sad")) %>%
  group_by(model, emo) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE), 
            sd_RMS = sd(zdiff, na.rm = TRUE), 
            n = n(), 
            stderr = sd_RMS/sqrt(n)) %>%
  ggplot(aes(x = emo, y = meanZ, group = model, colour = model)) +
  geom_point() +
  geom_line() +
  scale_colour_hp(option = "ravenclaw", alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, house = NULL) +
  geom_errorbar(aes(ymin = meanZ-stderr, ymax = meanZ+stderr), size = .4, width = .4) +
  theme_apa() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey") +
  scale_y_continuous(limits = c(-0.15, 0.25)) +
  labs(title = "Cheek", y = "Mean difference in muscle activity 
(baseline corrected z-score)", x = "Time post-stimulus presentation onset (ms)") +
  easy_x_axis_title_size(size = 16) +
  easy_y_axis_title_size(size = 16) +
  easy_text_size(size = 12) +
  easy_plot_legend_title_size(size = 16) +
  easy_plot_legend_size(size = 14) +
  easy_add_legend_title("Emotion") +
  easy_plot_title_size(size = 16) +
  easy_x_axis_labels_size(size = 12)

cplot7

ggsave("emoXmodel.png")
```



