---
title: "combine clean adult_child"
author: "Jen Richmond"
date: "01/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(naniar)
library(ggbeeswarm)
library(ggeasy)
library(readr)
library(readxl)
```

# Read in clean data

Using map to read in and bind together many csv files- notes from this blog post using option2A www.jenrichmond.rbind.io/post/use-map-to-read-many-csv-files

### read in child data
```{r message=FALSE, warning=FALSE}

data_path1 <- here("data", "clean_data")

files <- dir(data_path1, pattern = "*_child_*")

child_data <- files %>%
  map(~ read_csv(file.path(data_path1, .))) %>%
  reduce(rbind)



```

### read adult files
```{r message=FALSE, warning=FALSE}

data_path2 <- here("data", "clean_data")

files2 <- dir(data_path2, pattern = "*_adult_*")

adult_data <- files2 %>%
  map(~ read_csv(file.path(data_path2, .))) %>%
  reduce(rbind)

```

# create participant and condition columns out of filename

Use separate() to split the filename into  pp_no and condition and mutate with str_sub to drop the last 6 characters off the end of the values in the condition column to get rid of the .xlsx

```{r}
adult_cond <- adult_data %>%
  separate(file_name, into = c("pp_no", "model", "emotion"), sep = "_") %>% 
  mutate(emotion = str_sub(emotion, end = -6)) 

child_cond <- child_data %>%
  separate(file_name, into = c("pp_no", "model", "emotion"), sep = "_") %>% 
  mutate(emotion = str_sub(emotion, end = -6)) 
```


# bind child_cond and adult_cond together using rbind and then write csv
```{r}
child_adult_clean <- 
  rbind(child_cond, adult_cond) %>%
  write_csv(here("data", "adult_child_combined", "child_adult_clean.csv"))

```

