---
title: "4_clean_baseline"
output: html_document
---

# Load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(naniar)
library(ggbeeswarm)
library(ggeasy)
library(readr)
library(readxl)
library(janitor)
```



#read in clean data.csv

```{r message=FALSE, warning=FALSE}
clean_data <- read_csv(here("data", "adult_child_combined", "child_adult_clean.csv"))

```


# arrange by pp, emotion, muscle. 

Add an empty bl_outlier column 

```{r}
bl_data <- clean_data %>%
  filter(bin == "bin_0") %>%
  arrange(pp_no, emotion, muscle) %>%
  mutate(bl_outlier = "")

stim_data <- clean_data %>%
  filter(bin != "bin_0") %>%
  arrange(pp_no, emotion, muscle) %>%
  mutate(bl_outlier = "")
```
 

# add mean and sd columns 

and true false if bl_rms is > 1.5sd above the mean for the participant, emotion, muscle
```{r}

bl_stats <- bl_data %>%
  group_by(pp_no, emotion, muscle) %>%
  mutate(meanRMS = mean(rms), sdRMS = sd(rms)) %>%
  mutate(bl_outlier = if_else(rms > meanRMS + 1.5*sdRMS, "TRUE", "FALSE"))


```


# make outliter logical 

```{r}
bl_stats$bl_outlier <- as.logical(bl_stats$bl_outlier)

```

# count how many trials have bad baseline

```{r}
bl_stats %>%
  group_by(pp_no, emotion, muscle) %>%
  summarise(trialcount = n(), trialbad = sum(bl_outlier))

```


# drop extra variables

make bl_outlier as.character and bind stim and BL back together

```{r}
bl_bind <- bl_stats %>%
  select(pp_no:rms, bl_outlier)

stim_data$bl_outlier <- as.logical(stim_data$bl_outlier)

bl_stim <- bind_rows(bl_bind, stim_data) %>%
  arrange(pp_no, emotion, trial, muscle, bin_no) %>%
  fill(bl_outlier)

```

# filter out whole trials with bl outliers, write to csv 
```{r}
no_bl_outliers <- bl_stim %>%
  filter(bl_outlier == FALSE) %>%
  select(-bl_outlier)

no_bl_outliers %>% 
  write_csv(here("data", "adult_child_combined", "clean_no_bl_outliers.csv"))
```

# make a df with only outlier trials and write to csv
```{r}
just_bl_outliers <- bl_stim %>%
  filter(bl_outlier == TRUE)

just_bl_outliers %>%
  write_csv(here("data", "adult_child_combined", "clean_just_bl_outliers.csv"))


```

