---
title: "7_plotting"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r eval=FALSE}

library(devtools)

devtools::install_github("crsh/papaja")
```


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(papaja)
library(beepr)
```


# read bin screened data

```{r}
plot_data <- read_csv(here::here("data", "adult_child_combined", "zdiff_binscreened.csv"))

```

# fix bin values 

- drop diff bit from values in bin column, keep the last 4 char from diff_bin1
```{r}
plot_data$bin <- str_sub(plot_data$bin, -4)
```

# add emotion_type variable

```{r}
plot_data <- plot_data %>%
  mutate(emo_type = case_when(emotion == 121 ~ "child_happy", 
                              emotion == 323 ~ "child_angry", 
                              emotion == 424 ~ "child_fear", 
                              emotion == 525 ~ "child_sad", 
                              emotion == 131 ~ "adult_happy", 
                              emotion == 232 ~ "adult_angry", 
                              emotion == 434 ~ "adult_fear", 
                              emotion == 535 ~ "adult_sad"))
```

# fix data type
```{r}
plot_data$emo_type <- as.factor(plot_data$emo_type)

plot_data$trial <- as.factor(plot_data$trial)

plot_data$bin <- as.factor(plot_data$bin)

plot_data$muscle <- as.factor(plot_data$muscle)

glimpse(plot_data)

levels(plot_data$bin)
```

# BROW-ADULT

## plot brow for adult face data

### all emotions
```{r}
plot_data %>%
  filter(model == "adult", muscle == "brow") %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))

```

### just happy and angry
```{r}

plot_data %>%
  filter(model == "adult", muscle == "brow") %>%
  filter(emo_type %in% c("adult_happy", "adult_angry")) %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))

```

### just sad fear
```{r}
plot_data %>%
  filter(model == "adult", muscle == "brow") %>%
  filter(emo_type %in% c("adult_sad", "adult_fear")) %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))


```

```{r}
beep(1)
```

# BROW-CHILD

##plot brow for child face data

#### all emotions
```{r}
plot_data %>%
  filter(model == "child", muscle == "brow") %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```
#### just happy and angry
```{r}
plot_data %>%
  filter(model == "child", muscle == "brow") %>%
  filter(emo_type %in% c("child_happy", "child_angry")) %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))

```

#### just sad and fear

```{r}

plot_data %>%
  filter(model == "child", muscle == "brow") %>%
  filter(emo_type %in% c("child_sad", "child_fear")) %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in brow muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))

```

```{r}
beep(2)
```

# CHEEK-ADULT

## plot cheek for adult face data 

#### all emotions
```{r}
plot_data %>%
  filter(model == "adult", muscle == "cheek") %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```
#### just happy angry
```{r}
plot_data %>%
  filter(model == "adult", muscle == "cheek") %>%
  filter(emo_type %in% c("adult_happy", "adult_angry")) %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))

```

#### just sad fear

```{r}
plot_data %>%
  filter(model == "adult", muscle == "cheek") %>%
  filter(emo_type %in% c("adult_sad", "adult_fear")) %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))



```
```{r}
beep(3)
```


# CHEEK-CHILD
 
## plot cheek for child face data 

#### all emotions
```{r}
plot_data %>%
  filter(model == "child", muscle == "cheek") %>%
  group_by(emotion, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emotion, colour = emotion)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```

#### just happy angry
```{r}
plot_data %>%
  filter(model == "child", muscle == "cheek") %>%
  filter(emo_type %in% c("child_happy", "child_angry")) %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```

#### just sad fear
```{r}
plot_data %>%
  filter(model == "child", muscle == "cheek") %>%
  filter(emo_type %in% c("child_sad", "child_fear")) %>%
  group_by(emo_type, bin) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  labs(title = "mean difference in cheek muscle activity from baseline", subtitle = "response to emotion displayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))


```

```{r}
beep(4)
```


# ADULT-CHEEK-BROW

## plot brow and cheek together for adult

#### all emotion
```{r}
plot_data %>%
  filter(model == "adult") %>%
  group_by(emo_type, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to fear and sad diplayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```
### just happy angry
```{r}
plot_data %>%
  filter(model == "adult") %>%
  filter(emo_type %in% c("adult_happy", "adult_angry")) %>%
  group_by(emo_type, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to happy and angry diplayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```

### just fear and sad
```{r}
plot_data %>%
  filter(model == "adult") %>%
  filter(emo_type %in% c("adult_fear", "adult_sad")) %>%
  group_by(emo_type, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to fear and sad diplayed by adults") +
  scale_y_continuous(limits = c(-0.15, 0.25))


```

```{r}
beep(5)
```

# CHILD-CHEEK-BROW

## plot brow and cheek together for child

### all emotion

```{r}
plot_data %>%
  filter(model == "child") %>%
  group_by(emo_type, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to sad and fear diplayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))
```

### just happy angry
```{r}
plot_data %>%
  filter(model == "child") %>%
  filter(emo_type %in% c("child_happy", "child_angry")) %>%
  group_by(emo_type, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to happy and angry diplayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))

```

### just sad fear

```{r}
plot_data %>%
  filter(model == "child") %>%
  filter(emo_type %in% c("child_sad", "child_fear")) %>%
  group_by(emo_type, bin, muscle) %>%
  summarise(meanZ = mean(zdiff, na.rm = TRUE)) %>%
  ggplot(aes(x = bin, y = meanZ, group = emo_type, colour = emo_type)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~ muscle) +
  labs(title = "mean difference in brow and cheek muscle activity from baseline", subtitle = "response to sad and fear diplayed by children") +
  scale_y_continuous(limits = c(-0.15, 0.25))


```

```{r}
plot_data <- plot_data %>%
  write_csv(here::here("data", "adult_child_combined", "zdiff_binscreened_plot.csv"))
```

```{r}
beep(6)
```

