---
title: "8_analysing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The models in this RMD predict zdiff separately for 

- adultface_cheek
- childface_cheek
- adultface_brow
- childface_brow

Each model includes fixed effects of emotion (happy, angry, sad, fear) and bin and emotion * bin interaction, along with random intercepts for particpant and trial. 

The assumptions for each model are checked, but NOT corrected. 
These models also do not include slopes for fixed effects. 

# load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(ggplot2)
library(beepr)
```

# read in data

```{r}
df <- read_csv(here::here("data", "adult_child_combined", "zdiff_binscreened.csv"))
```

#fix data types, all chars to factors

```{r}


df <- df %>% mutate_if(is.character,as.factor)

# fix bin levels


df$bin <- fct_relevel(df$bin, c("diff_bin1", "diff_bin2", "diff_bin3", "diff_bin4", "diff_bin5", "diff_bin6", "diff_bin7", "diff_bin8", "diff_bin9", "diff_bin10"))

df$emotion <- as_factor(df$emotion)

levels(df$bin)  
levels(df$emotion)    

glimpse(df)
```

# CHEEK all emotion adult 


## make df
```{r}
adult_cheek <- df %>%
  filter(muscle == "cheek") %>%
  filter(model == "adult") %>%
  arrange(pp_no, model, emotion, trial, bin)

glimpse(adult_cheek)

levels(adult_cheek$emotion)

```



evidence of mimicry to happy would be evidenced by greater cheek activity over time (bin) for happy than angry

looking to predict zdiff from emotion (happy, angry), and bin (1-10) and their interaction, allowing intercepts to vary for participant and trial 

## fit model
```{r}
adultlm_model_cheek <- lmer(zdiff ~ emotion + bin + emotion*bin + (1|pp_no) + (1|trial), data = adult_cheek, REML = FALSE)

beep(1)
```

## use ANOVA to estimate effects 
```{r}
anova(adultlm_model_cheek)

```

## use summary to get coefficients 
```{r}
summary(adultlm_model_cheek)

```

## test cheek model assumptions

### plot residuals 
```{r}
plot(adultlm_model_cheek)

```

### qqplot 
```{r}
qqnorm(resid(adultlm_model_cheek))
qqline(resid(adultlm_model_cheek))
```

*YIKES!* this qq plot does not look good!!

# CHEEK all emotion child

## make df
```{r}
child_cheek <- df %>%
  filter(muscle == "cheek") %>%
  filter(model == "child") %>%
  arrange(pp_no, model, emotion, trial, bin)

glimpse(child_cheek)



levels(child_cheek$emotion)
```

## fit model
```{r}
childlm_model_cheek <- lmer(zdiff ~ emotion + bin + emotion*bin + (1|pp_no) + (1|trial), data = child_cheek, REML = FALSE)

beep(2)
```

## use ANOVA to estimate effects
```{r}
anova(childlm_model_cheek)
```

## use summary to get coefficients
```{r}
summary(childlm_model_cheek)
```

## test model assumptions

### plot residuals
```{r}
plot(childlm_model_cheek)
```

### qqplot
```{r}
qqnorm(resid(childlm_model_cheek))
qqline(resid(childlm_model_cheek))
```

# BROW all emotion adult

## make df
```{r}
adult_brow <- df %>%
  filter(muscle == "brow") %>%
  filter(model == "adult") %>%
  arrange(pp_no, model, emotion, trial, bin)

glimpse(adult_brow)

levels(adult_brow$emotion)
```

## fit model
```{r}
adultlm_model_brow <- lmer(zdiff ~ emotion + bin + emotion*bin + (1|pp_no) + (1|trial), data = adult_brow, REML = FALSE)

beep(3)
```

## use ANOVA to esitamte effects
```{r}
anova(adultlm_model_brow)
```

## use summary to get coefficients
```{r}
summary(adultlm_model_brow)
```

## check assumptions

### plot residuals
```{r}
plot(adultlm_model_brow)
```

### qqplot
```{r}
qqnorm(resid(adultlm_model_brow))
qqline(resid(adultlm_model_brow))
```

# BROW all emotion child 

## make df
```{r}
child_brow <- df %>%
  filter(muscle == "brow") %>%
  filter(model == "child") %>%
  arrange(pp_no, model, emotion, trial, bin)

glimpse(child_brow)

levels(child_brow$emotion)
```

## fit model
```{r}
childlm_model_brow <- lmer(zdiff ~ emotion + bin + emotion*bin + (1|pp_no) + (1|trial), data = child_brow, REML = FALSE)

beep(4)
```

## ANOVA to estimate effects
```{r}
anova(childlm_model_brow)
```

## use summary to get coefficients
```{r}
summary(childlm_model_brow)
```

## check assumptions

### plot residuals
```{r}
plot(childlm_model_brow)
```

### qqplot
```{r}
qqnorm(resid(childlm_model_brow))
qqline(resid(childlm_model_brow))
```

