---
title: "map_df clean dynamic"
author: "Jen Richmond"
date: "01/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Option 2. map_df: read,  clean, bind to df

map_df is like map except that rather than returning a list, it returns a dataframe. What if we use map_df to run clean_emg (not the write_csv version), would that bind everything into a df?? If its going to bind everything together, maybe we perhaps dont need to write individual clean files to csv, and them read them back in in order to do next step?


#### A. map read_excel

```{r message=FALSE, warning=FALSE}
list_raw_emg <- file_list %>% 
  map(~ read_excel(path = here("R_cleaning", "data", "raw_data", "faces", .x), range = "A2:AE13")  %>%
        mutate("file_name" = .x))

# get first item of list for testing
emg1 <- list_raw_emg[[1]]

```

#### B. map_df clean_emg
```{r}
df_clean_emg <- list_raw_emg %>%
  map_df(~ clean_emg(.x))

```

## bind pp604_429 with full faces clean data set
NOTe: run cleanup RAW eg pp604_429 before this step!

```{r}
final_clean_faces <- bind_rows(df_clean_emg, test_long)

final_clean_faces$rms <- as.numeric(final_clean_faces$rms)
final_clean_faces$bin <- as.factor(final_clean_faces$bin)
final_clean_faces$trial <- as.factor(final_clean_faces$trial)
final_clean_faces$muscle <- as.factor(final_clean_faces$muscle)

write_csv(final_clean_faces, here("R_cleaning", "data", "clean_data", "faces_clean.csv"))


```

