---
title: "add filename"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# load packages
```{r}
library(readxl)
library(tidyverse)
library(here)
library(janitor)

```

# call functions
```{r}

source(here("R_cleaning", "cleanwrite_emg_functions.R"))
```

SOlution from https://stackoverflow.com/questions/47540471/load-multiple-excel-files-and-name-object-after-a-file-name

# set up path and files list

```{r}
filepath <- here("R_cleaning", "data", "raw_data", "non-faces")

file_list <- list.files(path = filepath, pattern='*.xlsx')


```

# Option 1. map: read, clean, write to csv

This option reads the dirty xlsx files into a list, runs cleanwrite_emg on that list, which returns exported clean csv files and a list with clean data in each list item. How...?

the map function takes a list (in this case the list of files) and runs a function (in this case read_excel + mutate(filename)) across all of them. 

map will return a list, in this case a list containing each of the read in excel files + a filename column as a separate item. 

purrr loves lists, once all the files are read in as list items, can use map again (or maybe even map_df- which returns a dataframe- see option 2) to run cleanwrite_emg across all items in the list?

#### A. map read_excel

updated 21/5/2020 advice from Jenny Bryan, option 1 https://jenrichmond.github.io/map_excel_reprex/
```{r message=FALSE, warning=FALSE}
list_raw_emg <- file_list %>% 
  map(~ read_excel(path = here("R_cleaning", "data", "raw_data", "non-faces", .x), range = "A2:AE13")  %>%
        mutate("file_name" = .x))

```

```{r}
# get first item of list for testing
rawemg1 <- list_raw_emg[[1]]
```


#### B. map cleanwrite_emg
Run cleanwrite_emg on list of files using map, returns a list. Each item in the list is a cleaned file AND each is written to csv in the clean_data folder. 

```{r}
list_cleanwrite_emg <- list_raw_emg %>%
  map(~ cleanwrite_emg(.x))
```


#### C. Check the list items 

did you get what you want? look at the 1st item from the cleanemg emglist. There should also be clean csv files in your folder. 
```{r}
cleanemg1 <- list_cleanwrite_emg[[1]]
```

YES!

# Option 2. map_df: read,  clean, bind to df

map_df is like map except that rather than returning a list, it returns a dataframe. What if we use map_df to run clean_emg (not the write_csv version), would that bind everything into a df?? If its going to bind everything together, maybe we perhaps dont need to write individual clean files to csv, and them read them back in in order to do next step?


#### A. map read_excel

```{r}
list_raw_emg <- file_list %>% 
  map(~ read_excel(path = here("R_cleaning", "data", "raw_data", "non-faces", .x), range = "A2:AE13")  %>%
        mutate("file_name" = .x))

# get first item of list for testing
emg1 <- list_raw_emg[[1]]

```

#### B. map_df clean_emg
```{r}
df_clean_emg_nonfaces <- list_raw_emg %>%
  map_df(~ clean_emg(.x))
```

```{r}

df_clean_emg_nonfaces$rms <- as.numeric(df_clean_emg_nonfaces$rms)
df_clean_emg_nonfaces$bin <- as.factor(df_clean_emg_nonfaces$bin)
df_clean_emg_nonfaces$trial <- as.factor(df_clean_emg_nonfaces$trial)
df_clean_emg_nonfaces$muscle <- as.factor(df_clean_emg_nonfaces$muscle)


write_csv(df_clean_emg_nonfaces, here("R_cleaning", "data", "clean_data"), path = "non-faces_clean.csv")
```

